---
title: "04_Var_envi"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


##### Script 04: Environmental variables selection #####

###################################################
#      Authors: Eddie Pérochon & Maël Doré        #
#      Contact: eddie.perochon@hotmail.com        #
###################################################


### Goals = 
  # Import environmental data, set extent and resolution of study area, select variables, and stack them
###


### Inputs
   # Climatic & elevation data from WorldCLIM
   # Forest cover data from Landsat Vegetation Continuous Fields (Sexton et al., 2013)

###

### Outputs

   # Final environmental stack
   # Climatic variable selection assessment: HAC dendrogram, PCA correlation circle, RDA results
   # Correlation matrix for final stack
###

```{r}
# Remove environment
rm(list = ls())

# Load libraries
library(raster)
```


```{r}
Donlev<-function(x) {levels(factor(x))}
```

```{r}
My_crop<-function(x){
xmin = -133 ; xmax = -30 ; ymin = -37 ; ymax = 48
e <- extent(c(xmin,xmax,ymin,ymax))

cropped<-crop(x, e)

return(cropped)}
```

```{r}
RDA_fct<-function(x,y){
Y4 <- x[,y] # Explanatory variables = set of selected variables
X4 <- x[,-y] # Responses variables = other climatic variables

RDA <- rda(X = X4, Y = Y4 , scale = T) 
res_RDA <- round(summary(RDA)$cont[[1]][2:3,]*100, 1) ; res_RDA # To see proportions of constrained and unconstrained inertia
r2_RDA <- round(RsquareAdj(RDA)$adj.r.squared, 3) ; r2_RDA

# Test significiance of the RDA with permutation on the pseudo F-ratio
F_test_RDA <- anova.cca(object = RDA, permutations = 1000) ; F_test_RDA 
F_value <- round(F_test_RDA$F[1], 0)
p_value <- round(F_test_RDA$`Pr(>F)`[1], 3)


### PCA on 4 selected bioclim var.
PCA_vars <-  dudi.pca(df = x[,y], center = T, nf = 3, scannf = F) # Generate the PCA

# Compute % variance explained by each PC axis.
var_perc <- round(PCA_vars$eig/sum(PCA_vars$eig)*100, 1) 
cum_var_perc <- round(cumsum(var_perc),1) # Cumulated explained variance
PCA_vars$co # Correlation: variables ~ PC axis


original_int_margins <- par()$mar
original_ext_margins <- par()$oma
par(oma = c(0,2,2,3), mar = c(5.1,7,4.1,7), xpd=NA)
s.corcircle(PCA_vars$co, xax=1, yax=2, clabel = 1.5)
text(x = 1.2 , y = -0.8, labels = paste0("PC1: ", var_perc[1], "%"), font = 2, cex = 1.3)
text(x = -1.4 , y = -0.6, font = 2, cex = 1.3, srt = 90,
     labels = paste0("PC2: ", var_perc[2], "%\nSum: ", cum_var_perc[2], "%"))
text(x = 0 , y = 1.1, font = 2, cex = 1.3,
     labels = paste0("RDA: ", res_RDA[2, length(y)], "%, F = ", F_value, ", p = ", p_value))
par(mar = original_int_margins, oma = original_ext_margins, xpd = F)

return(res_RDA)
}
```


```{r}
VIF_fct<-function(x){ 
  # Need to subsample for only 10000 pixels
data_full <- data.frame(rep(NA,10000))

index.sample <- sample(x = which(!is.na(x[[1]]@data@values)), size = 10000) # Get index of cells which are not NA

for (i in 1:(length(names(x)))) {
  data_full[,i] <- x[[i]]@data@values[index.sample] # Retrieve 10000 values from each layer
}
names(data_full) <- names(x)

# Check correlation, including Elevation and Forests
cor(data_full)

# Rarity::corPlot(df = data_full, method = "spearman")

library(corrgram)

corrgram::corrgram(x = data_full, type = "data", order = T,
                   lower.panel = panel.pie,  upper.panel = panel.conf, diag.panel = panel.density,
                   col.regions = colorRampPalette(c("navy", "royalblue", "white", "salmon", "red"))) # pour plotter les correlations entre variables de manière stylée

# Check VIF, including Elevation and Forests
usdm::vif(data_full)

}

```


```{r}
###### 1/ Import Climatic data ######

# 1.1/ Resolution = 10min ####

# Load a Bioclim layer to use as mask to define terrestrial boundaries
    BioClim_mask <- stack(raster("Variables bioclim/bioclim_var/wc2.1_5m_bio_1.tif"))
BioClim_mask<-My_crop(BioClim_mask)

# plot(BioClim_mask)

# Load World Clim stack
climate.vars <- paste0(1:19)
envData <- NA
for (j in climate.vars) {
  
  if(j == climate.vars[1]) { # Create the stack
    
    envData <- stack(raster(paste0("Variables bioclim/bioclim_var/wc2.1_5m_bio_", j,".tif")))
  
  } else { # Add layer iteratively
     
    envData <- addLayer(envData, raster(paste0("Variables bioclim/bioclim_var/wc2.1_5m_bio_", j,".tif")))
    
  }
}
names(envData) <- paste0("bio", 1:19) # Create layer name

save(envData, file = "../input_data/envData/envData.RData")
saveRDS(envData, file = "../input_data/envData/envData.rds")

```

```{r}
###Add Forest & altitude
#Alt 5m
envfullData <- addLayer(envData, raster("Variables bioclim/bioclim_elev/wc2.1_5m_elev.tif"))
names(envfullData[[20]])<-"elev"

###Crop our zone
EnvCropped<-My_crop(envfullData)

###Forest, px=4.5km, already cropped but not exact so resample
Forest_layer <- raster("Variables bioclim/nasa_forestcover/VCF_Export.tif")

Forest_layer <- resample(Forest_layer, EnvCropped, method="bilinear")

EnvCropped <- addLayer(EnvCropped, Forest_layer)
names(EnvCropped[[21]])<-"forest"

BioClim_mask

```

```{r}
Masked_env <- mask(EnvCropped, BioClim_mask) # Apply Bioclim mask to keep only terrestrial data


save(Masked_env, file = "../input_data/envData/All_variables.RData")
saveRDS(Masked_env, file = "../input_data/envData/All_variables.rds")

```

```{r}
###Mollweide proj
All_variables<-readRDS("../input_data/envData/All_variables.rds")
All_variables_MW <- projectRaster(from = All_variables, 
                           method = "bilinear", # Method for interpolation => "ngb" = nearest neighbor for qualitative (or discrete) variables . "bilinear" = for quantitative variables
                           crs = "+proj=moll +lon_0=-79 +lat_0=6 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=km +no_defs", # If you have the CRS arguments
                           alignOnly = F)

plot(All_variables_MW[[1]])
```


```{r}
###raster to resample and make cells of similar sizes
grid_filter<-raster(nrows=347, ncol=340, ymn=(-4494.85), ymx=5705.15, xmn=(-5456.522), xmx=4953.478, crs = "+proj=moll +lon_0=-79 +lat_0=6 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=km +no_defs")

All_variables_MW_RS <- resample(x = All_variables_MW, y = grid_filter, method = "bilinear")

save(All_variables_MW_RS, file = "../input_data/envData/All_variables_MW_RS.RData")
saveRDS(All_variables_MW_RS, file = "../input_data/envData/All_variables_MW_RS.rds")

```


```{r}
All_variables_MW_RS<-readRDS("../input_data/envData/All_variables_MW_RS.rds")

### 2.1/ HAC clustering on environmental variables ####

library(virtualspecies)
source(file = "../functions/raster_multicollinearity.R")

raster_multicollinearity(raster.stack = All_variables_MW_RS[[1:19]], method = "pearson", multicollinearity.cutoff = 0.6, sample.points = T, nb.points = 10000, plot = T)

dev.off()
```

```{r}
### 2.2/ PCA and RDA on environmental variables ####

library(ade4)
library(vegan)

# Need to subsample for only 10000 pixels
data_clim <- data.frame(rep(NA,10000))

All_variables_MW_RS<-readAll(All_variables_MW_RS)

set.seed(5452)
index.sample <- sample(x = which(!is.na(All_variables_MW_RS[[1]]@data@values)), size = 10000) # Get index of cells which are not NA

for (i in 1:(length(names(All_variables_MW_RS))- 2)) {
  data_clim[,i] <- All_variables_MW_RS[[i]]@data@values[index.sample] # Retrieve 10000 values from each layer
}
names(data_clim) <- names(All_variables_MW_RS[[1:19]])


```

```{r}
### PCA on all climatic variables

PCA_full <-  dudi.pca(df = data_clim, center = T, nf = 3, scannf = F) # Generate the PCA

# Compute % variance explained by each PC axis
var_perc <- round(PCA_full$eig/sum(PCA_full$eig)*100, 1) 
cum_var_perc <- round(cumsum(var_perc), 1) # Cumulated explained variance
PCA_full$co # Correlation: variables ~ PC axis

# Plot correlation circle of PCA with results of RDA


original_ext_margins <- par()$oma
original_int_margins <- par()$mar
par(oma = c(0,2,0,3), mar = c(5.1,7,4.1,7), xpd=NA)
s.corcircle(PCA_full$co, xax=1, yax=2, clabel = 1.5)
text(x = c(-1, 0), labels = paste0("PC1: ", var_perc[1], "%"), font = 2, cex = 1.3)
text(x = -1.2 , y = -0.6, adj = c(0, 0), labels = paste0("PC2: ", var_perc[2], "%\nSum: ", cum_var_perc[2], "%"), font = 2, cex = 1.3, srt = 90)
par(mar = original_int_margins, oma = original_ext_margins, xpd = F)

original_ext_margins <- par()$oma
original_int_margins <- par()$mar
par(oma = c(0,2,0,3), mar = c(5.1,7,4.1,7), xpd=NA)
s.corcircle(PCA_full$co, xax=1, yax=3, clabel = 1.5)
text(x = c(-1, 0), labels = paste0("PC1: ", var_perc[1], "%"), font = 2, cex = 1.3)
text(x = -1.2 , y = -0.6, adj = c(0, 0), labels = paste0("PC3: ", var_perc[3], "%\nSum: ", cum_var_perc[3], "%"), font = 2, cex = 1.3, srt = 90)
par(mar = original_int_margins, oma = original_ext_margins, xpd = F)

original_ext_margins <- par()$oma
original_int_margins <- par()$mar
par(oma = c(0,2,0,3), mar = c(5.1,7,4.1,7), xpd=NA)
s.corcircle(PCA_full$co, xax=2, yax=3, clabel = 1.5)
text(x = c(-1, 0), labels = paste0("PC2: ", var_perc[2], "%"), font = 2, cex = 1.3)
text(x = -1.2 , y = -0.6, adj = c(0, 0), labels = paste0("PC3: ", var_perc[3], "%\nSum: ", cum_var_perc[3], "%"), font = 2, cex = 1.3, srt = 90)
par(mar = original_int_margins, oma = original_ext_margins, xpd = F)

```

```{r}
## Compute RDA for 5 variables (BIO1, BIO2, BIO12, BIO15, BIO5) = Isothermality, to test representativity

names(data_clim[,20:21])<-c("elev","forest")
vars_index <- c(1,2,12,15,20,21) # Indices of climatic variable to keep
RDA_fct(data_clim, vars_index)
```


Var selected: BIO (1,2,5,12,15), elev and forest

```{r}
Var_stack_final<-All_variables_MW_RS[[c(1,2,5,12,15,20,21)]]
```

```{r}
#On test le VIF + correl (voir dans la fonction)
VIF_fct(Var_stack_final)
```

```{r}
##Scatterplot, recherche de corrélations entre variables
pairs(Var_stack_final, v=NULL, pa='pa', hist=TRUE, cor=TRUE)

#Gros VIF+ bc de corrélation = on regarde sans la var 5
```

```{r}
### Compute RDA for 4 variables (BIO1, BIO2, BIO12, BIO15), to test representativity

vars_index <- c(1,2,12,15,) # Indices of climatic variable to keep
RDA_fct(data_clim, vars_index)


```
```{r}
Var_stack_final<-Var_stack_final[[-3]]
VIF_fct(Var_stack_final)

##VIF bien meilleur + moins de corrélations + interpretation limitée: on enlève 5
```

```{r}
####Stack final avec 4 BIO + foret + elev
Var_stack_final <- virtualspecies::synchroniseNA(Var_stack_final)
VIF_fct(Var_stack_final)


save(Var_stack_final, file = "../input_data/envData/Envstack.RData")
saveRDS(Var_stack_final, file = "../input_data/envData/Envstack.rds")
```

