---
title: "06_Environmental outliers"
output: html_document
---


##### Script 06: Remove environmental outliers #####

###################################################
#      Authors: Eddie Pérochon & Maël Doré        #
#      Contact: eddie.perochon@hotmail.com        #
###################################################


### Goals = 
# Clean occurrences that are aberrant in terms of environmental values


### Inputs =

#Occurrence data rasterized for each subspecies
#Environmental stack of selected variables

###

### Outputs
# List of outliers
# Outliers evaluation files
# Occurrences dataset which will be used for modelling

###

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
###clean envi + packages
rm(list = ls())

library(ade4)
library(dplyr)
library(sf)
library(raster)
library(rgl)
library(FactoMineR)
library(factoextra)
library(stringr)

```

```{r}
# Function to check for variance in dataset
zero_range <- function(x, tol = .Machine$double.eps ^ 0.5) {
  if (length(x) == 1) return(TRUE)
  x <- range(x) / mean(x)
  isTRUE(all.equal(x[1], x[2], tolerance = tol))
}
```

```{r fonction pour regarder les levels}
Donlev<-function(x) {levels(factor(x))}

```

```{r}
#Files
load(file = "../input_data/occurences_df/list_occ_wt_modeletype.RData")
list_occ$code_unit <-str_replace(list_occ$code_unit, "sp_nov", "sp.nov")
load(file = "../input_data/occurences_df/list_occ_vec.RData")
list_occ_vec <-str_replace(list_occ_vec, "sp_nov", "sp.nov")

load(file = "../input_data/envData/Envstack.RData")


Full_env <- Var_stack_final
```


```{r}
###Load a df of every occurences after rastering

for (k in seq_along(list_occ_vec)){
  unit<-list_occ_vec[k]
  if (k==1)
  {load(file =paste0("../input_data/Species_data/Spatial_Points_Objects/occurrences_",unit,".RData"))
    Rasterized_df<-as.data.frame(unit_points)
    Rasterized_df$Tag<-unit
    print(paste0("Done for ", unit," ", k,"/",length(list_occ_vec))) 
    } 
  else {
   load(file =paste0("../input_data/Species_data/Spatial_Points_Objects/occurrences_",unit,".RData"))
    unit_points<-as.data.frame(unit_points)
    unit_points$Tag<-unit
    names(unit_points)<-c("Occurrence", "x", "y", "Tag")
   Rasterized_df <- rbind(Rasterized_df, unit_points)
    print(paste0("Done for ", unit," ", k,"/",length(list_occ_vec)))  
    }
}
Rasterized_df<- merge(Rasterized_df, list_occ[,3:8], by.x="Tag", by.y="code_unit")


save(Rasterized_df, file ="../input_data/occurences_df/Occ_used_for_SDM.RData")

saveRDS(Rasterized_df, file ="../input_data/occurences_df/Occ_used_for_SDM.RDS")
    

```

```{r}
#Load the df and make a list of species
Occ_used_for_SDM<-readRDS("../input_data/occurences_df/Occ_used_for_SDM.RDS")
Occ_used_for_SDM$Tag <-str_replace(Occ_used_for_SDM$Tag, "sp_nov", "sp.nov")
Occ_used_for_SDM$ID_obs<-1:nrow(Occ_used_for_SDM)

Occ_used_for_SDM <- Occ_used_for_SDM %>%
  tidyr::separate(Tag, c("genus", "sp", "ssp"), "_", remove=F)%>%
  tidyr::unite( "Sp_ID",c(genus, sp),sep="_", remove=F)

Occ_used_for_SDM$ssp[is.na(Occ_used_for_SDM$ssp)==TRUE]<-""

list_species<-Donlev(Occ_used_for_SDM$Sp_ID)
```




```{r}
# ACP initiale pour le 3D plot env.

data_full <- data.frame(rep(NA,10000)) # Need to subsample for only 10000 pixels

index.sample <- sample(x = which(!is.na(Full_env[[1]]@data@values)), size = 10000) # Get index of cells which are not NA

for (i in 1:(length(names(Full_env)))) {
  data_full[,i] <- Full_env[[i]]@data@values[index.sample] # Retrieve 10000 values from each layer
}
names(data_full) <- names(Full_env)[1:length(names(Full_env))]

data_full <- data_full[,-which(names(data_full) == "elev")] # Remove Elevation

ACP <-  dudi.pca(df = data_full, center = T, nf = 2, scannf = F) # G?n?re l'ACP
# round(ACP$eig/sum(ACP$eig)*100,3) # % variances expliqu?e par les axes : 1e = 62,8% ; 2e = 24,9% ; 3e = 6.0%
# cumsum(round(ACP$eig/sum(ACP$eig)*100,3)) # Variance expliqu?e cumulative : 1e = 62,8%, 1+2e = 87,7% ; 1+2+3e = 93,7%
# ACP$co # Correlations variables ~ PCAxis

vec <- ACP$c1[,1:2] # Extract des Eigenvectors pour pouvoir projeter des nouvelles occurences sur les 2 premiers axes
get_eigenvalue(ACP) # valeur des composantes principales


# Tableau final pour stocker les infos d'outliers
names(Full_env)

Outliers.index <- data.frame(Tag=character(), ID_obs=character(), bio1=numeric(), bio2=numeric(), bio12=numeric(), bio15=numeric(), elev=numeric(), forest=numeric())
Occ_used_for_SDM$outlier_maha <- F

# Librairies and parameters for 3D plots
library(rgl)
zoom <-  1
userMatrix <- matrix(data = c(0.8154871, 0.5784692, 0.01883241, 0, -0.1358215, 0.1596396, 0.97778738, 0, 0.5626130, -0.7999308, 0.20875259, 0, 0, 0, 0, 1), nrow = 4, ncol = 4, byrow =T)
windowRect <- c(34,  57, 533, 551)
viewport <-  c(0, 0, 499, 494) ; names(viewport) <- c("x","y", "width", "height")


```


```{r}

#####Distance de mahalanobis & envi outliers####


for (j in 1:nrow(list_occ)) {
  Tag <- list_occ$code_unit[j]
  
  Dataset <- Occ_used_for_SDM[Occ_used_for_SDM$Tag == Tag,] # Extraction des occurrences par unit
  
  if (nrow(Dataset)>2) { # Mahalanobis distance cannot be computed for 2 points

    
    Env.table <- raster::extract(x = Full_env, y = Dataset[,c("x","y")]) # Extraction des valeurs 
    index.error <- which(!complete.cases(Env.table)) # Extraction des occurrences en erreur
    
    # R?cup?ration d'infos dans les pixels les plus proches de l'occurrence en erreur
    for (i in index.error) {
      Error.occ <- Env.table[i,]
      buffer <- 5000  # Premier buffer = 5km
      while (anyNA(Error.occ)) { # Elargit le buffer tant que l'on pas r?cup?r? des donn?es
        Error.occ <- unlist(raster::extract(x = Full_env, y = Dataset[i,c("x","y")], buffer = buffer, fun = mean))
        buffer <- buffer + 5000 # Nouveau buffer = + 5km
      }
      cat("Buffer for",as.character(list_occ$Tag[j]),"=",buffer/1000,"km\n") # Check la largeur finale du buffer
      Env.table[i,] <- Error.occ # Ecrit l'information
    }
    Env.table.orig <- Env.table # Stocke les valeurs non standardis?es
    
    # Standardisation des variables pour ?viter le probl?me d'?chelle lors du calcul de distance
    if(sum(apply(X = Env.table, MARGIN = 2, FUN = zero_range))==0) { # To check for the existence of variance in all variables
      Env.table <- as.data.frame(scale(Env.table, center = T, scale = T))
      
      if(det(as.matrix(cov(Env.table)))>2e-16) { # To avoid error with matrix that cannot be inverted
        # Calculate Mahalanobis Distance
        m_dist <- mahalanobis(Env.table, colMeans(Env.table), cov(Env.table))
        Env.table$m_dist <- round(m_dist, 2)
        
        # hist(Env.table$m_dist)
        # head(Env.table[order(Env.table$m_dist, decreasing = T),])
        
        # Mahalanobis Outliers for p = 7 = nb of env. variables
        p <- 7
        thres <- qchisq(p= 0.9999999, df = p-1) # Follow a Khi? distri for p-1 df (Etherington, 2019 => distri of p df !!!)
        Env.table$outlier_maha <- Env.table$m_dist > thres
        
        ### Tracer la loi de distri et les outliers sur le plot
        # x <- seq(0, max(Env.table$m_dist[Env.table$outlier_maha]*1.1), length=1000) ; y <- dchisq(x, df = p-1)
        # plot(x, y, type="l", lwd=1)
        # points(x = Env.table$m_dist[Env.table$outlier_maha], y = rep(0.01,sum(Env.table$outlier_maha)), pch = 16, cex = 1.2, col = "red")
        # segments(x0 = Env.table$m_dist[Env.table$outlier_maha], y0 = rep(0.01,sum(Env.table$outlier_maha)),
        #          x1 = Env.table$m_dist[Env.table$outlier_maha], y1 = rep(0,sum(Env.table$outlier_maha)), col = "red", lwd = 2)
        # abline(v=thres, col = "red", lty = 2)
        
        ### Liste des outliers
        if (sum(Env.table$outlier_maha) > 0) { # Si il y a des outliers
          if (sum(Env.table$outlier_maha) == 1) {
            New.outliers <- as.data.frame( t (c (as.character(Dataset$Tag[Env.table$outlier_maha]) , as.character(Dataset$ID_obs[Env.table$outlier_maha]), Env.table.orig[Env.table$outlier_maha,]))) # G?n?rer le tableau des outliers
          }else{
            New.outliers <- as.data.frame( cbind (as.character (Dataset$Tag[Env.table$outlier_maha ]) , as.character(Dataset$ID_obs[Env.table$outlier_maha]),
                                                  Env.table.orig[Env.table$outlier_maha,] 
                                                  )) # G?n?rer le tableau des outliers
          }
          names(New.outliers) <- names(Outliers.index)
          Outliers.index <- rbind(Outliers.index, New.outliers) # Ajouter au tableau existant
          Occ_used_for_SDM[Occ_used_for_SDM$ID_obs %in% New.outliers[,2],"outlier_maha"] <- T # Stocker l'info dans le dataset
        }
        
        ### 3D plot only if outliers !
        
        if (sum(Env.table$outlier_maha) > 0) {
          coords <- as.matrix(Env.table[,names(data_full)])%*%as.matrix(vec)
          coords <- as.data.frame(cbind(coords,Env.table$elev)) ; names(coords) <- c("PC1", "PC2", "elev")
          open3d(zoom = 1, userMatrix = userMatrix, windowRect=windowRect, viewport=viewport) # Ouvre la fen?tre 3D avec une orientation d?finie
          plot3d(x = coords, type = "n") # To generate the axis
          # Plot des outliers de la base 
          text3d(x = coords[(Env.table$outlier_maha),], texts = Dataset$ID_obs[(Env.table$outlier_maha)], col = "red", alpha = 1) # To add the labels in the desired color in the 3D plot
          #text3d(x = coords[(Env.table$outlier_maha),], texts = Dataset$Tag[(Env.table$outlier_maha)], col = "red", alpha = 1) # To add the labels in the desired color in the 3D plot
          points3d(x = coords, col=c("black","red")[Env.table$outlier_maha+1], size=5) # To add points in the desired color in the 3D plot
  
        
          rgl.snapshot(filename = paste0("../Maps/Outliers_env/3D_plot/",Tag,".png"), top =T)
          rgl.close()
        }
      }
    }
  }
  if (j%%10 == 0)  { # Print incr?ment seulement tous les 10
    print(j)
  }
}
```

```{r}

####Map all occurences

###Complete outlier_maha column
Occ_used_for_SDM$outlier_maha[is.na(Occ_used_for_SDM$outlier_maha==TRUE)]<-FALSE

# Altitude
Map_elev <- Full_env[[5]]

for (i in 1:length(list_species)){
  sp <- list_species[i]
  ssp.set <- Occ_used_for_SDM[ Occ_used_for_SDM$Sp_ID==sp ,c("x","y","ssp","Mimicry_ring")]

jpeg(filename = paste0("../Maps/Occurences_maps/By_sub.species/Full_extent/",sp,".jpeg"), quality =100) 
plot(Map_elev, main = sp)
points(ssp.set, col = 1, pch = 16, cex = 0.6)
points(ssp.set, col = as.numeric(factor(ssp.set$ssp))+1, pch =16, cex = 0.3)
legend(legend = Donlev(ssp.set$ssp), pch = 16, pt.cex = 1.3, col = 2:(1+length(Donlev(ssp.set$ssp))), x = "bottomleft", cex = 0.9, bty ="o")
dev.off()


jpeg(filename = paste0("../Maps/Occurences_maps/By_mimic/Full_extent/",sp,".jpeg"), quality =100) 
plot(Map_elev, main = sp)
points(ssp.set, col = 1, pch = 16, cex = 0.6)
points(ssp.set, col = as.numeric(factor(ssp.set$Mimicry_ring))+1, pch = 16, cex = 0.3)
legend(legend = Donlev(ssp.set$Mimicry_ring), pch = 16, pt.cex = 1.3, col = 2:(1+length(Donlev(ssp.set$Mimicry_ring))), x = "bottomleft", cex = 0.9, bty ="o")
dev.off()
}
```

```{r}
###Mimicry ring mapping
list_mimicry<-Donlev(Occ_used_for_SDM$Mimicry_ring)

for (i in 1:length(list_mimicry)){
  mr <- list_mimicry[i]
  mr.set <- Occ_used_for_SDM[ Occ_used_for_SDM$Mimicry_ring==mr ,c("x","y","Tag","Mimicry_ring", "Sp_ID")]

jpeg(filename = paste0("../Maps/Occurences_maps/Mimicry_rings/By_ssp/",mr,".jpeg"), quality =100) 
plot(Map_elev, main = mr)
points(mr.set, col = 1, pch = 16, cex = 0.6)
points(mr.set, col = as.numeric(factor(mr.set$Tag))+1, pch =16, cex = 0.3)
legend(legend = Donlev(mr.set$Tag), pch = 16, pt.cex = 1.3, col = 2:(1+length(Donlev(mr.set$Tag))), x = "bottomleft", cex = 0.9, bty ="o")
dev.off()


jpeg(filename = paste0("../Maps/Occurences_maps/Mimicry_rings/By_sp/",mr,".jpeg"), quality =100) 
plot(Map_elev, main = mr)
points(mr.set, col = 1, pch = 16, cex = 0.6)
points(mr.set, col = as.numeric(factor(mr.set$Sp_ID))+1, pch = 16, cex = 0.3)
legend(legend = Donlev(mr.set$Sp_ID), pch = 16, pt.cex = 1.3, col = 2:(1+length(Donlev(mr.set$Sp_ID))), x = "bottomleft", cex = 0.9, bty ="o")
dev.off()
}

```



```{r}


###  outliers in geographical space, per species


# Maps on full study area, by mimicry
for (i in 1:length(list_species)) {
  sp <- list_species[i]
  sp.set <- Occ_used_for_SDM[Occ_used_for_SDM$Sp_ID==sp ,c("x","y","Mimicry_ring","outlier_maha")]
  sp.set.outliers <- Occ_used_for_SDM[(Occ_used_for_SDM$Sp_ID==sp) & (Occ_used_for_SDM$outlier_maha==T), c("x","y","Mimicry_ring")]
  
  if (nrow(sp.set.outliers)>0) { # Seulement si il y a des outliers
    # Dans le dossier par types de maps
    jpeg(filename = paste0("../Maps/Outliers_env/By_mimic/Full_extent/",sp,".jpeg"), quality =100) 
   
    points(sp.set, col = 1, pch = 16, cex = 0.6)
    points(sp.set, col = as.numeric(factor(sp.set$Mimicry_ring))+1, pch = 16, cex = 0.3)
    points(sp.set.outliers, col = 1, pch =16, cex = 1.3)
    col.outliers <- as.numeric(factor(sp.set$Mimicry_ring))+1
    points(sp.set.outliers, col = col.outliers[sp.set$outlier_maha], pch =16, cex = 0.9)
    legend(legend = Donlev(sp.set$Mimicry_ring), pch = 16, pt.cex = 1.3, col = 2:(1+length(Donlev(sp.set$Mimicry_ring))), x = "bottomleft", cex = 0.9, bty ="o")
    dev.off()
    
    # Dans le dossier par esp?ces
    file.copy(from =  paste0("../Maps/Outliers_env/By_mimic/Full_extent/",sp,".jpeg"), to = paste0(getwd(),"/Maps/By_sp/",sp,"/Outliers_env_By_mimic_Full_extent_",sp,".jpeg"), overwrite = T)
  }
  
  if (i%%10 == 0)  { # Print incr?ment seulement tous les 10
    print(i)
  }
}
```

```{r}


# Maps on full study area, by sub.species
for (i in 1:length(list_species)){
sp <- list_species[i]
  ssp.set <- Occ_used_for_SDM[ Occ_used_for_SDM$Sp_ID==sp ,c("x","y","ssp","outlier_maha")]
  ssp.set.outliers <- Occ_used_for_SDM[ (Occ_used_for_SDM$Sp_ID==sp) & (Occ_used_for_SDM$outlier_maha==T), c("x","y","ssp","outlier_maha")]
  
  if (nrow(ssp.set.outliers)>0) { # Seulement si il y a des outliers
    # Dans le dossier par types de maps
    jpeg(filename = paste0("../Maps/Outliers_env/By_sub.species/Full_extent/",sp,".jpeg"), quality =100) 
    plot(Map_elev, main = sp)
    points(ssp.set, col = 1, pch = 16, cex = 0.6)
    points(ssp.set, col = as.numeric(factor(ssp.set$ssp))+1, pch =16, cex = 0.3)
    points(ssp.set.outliers, col = 1, pch = 16, cex = 1.3)
    col.outliers <- as.numeric(factor(ssp.set$ssp))+1
    points(ssp.set.outliers, col = col.outliers[ssp.set$outlier_maha], pch =16, cex = 0.9)
    legend(legend = Donlev(ssp.set$ssp), pch = 16, pt.cex = 1.3, col = 2:(1+length(Donlev(ssp.set$ssp))), x = "bottomleft", cex = 0.9, bty ="o")
    dev.off()
    
    # Dans le dossier par esp?ces
    file.copy(from =  paste0("../Maps/Outliers_env/By_sub.species/Full_extent/",sp,".jpeg"), to = paste0(getwd(),"/Maps/By_sp/",sp,"/Outliers_env_By_sub.species_Full_extent_",sp,".jpeg"), overwrite = T)
  }
  if (i%%10 == 0)  { # Print incr?ment seulement tous les 10
    print(i)
  }
}
```


```{r}
###Delete outliers from big DF and unit_points + change model type if needed
Occ_used_for_SDM<-Occ_used_for_SDM[Occ_used_for_SDM$outlier_maha==FALSE,] #Delete on bigDF
list_occ$N.obs_envOtl<-NA #New column in list_occ to stock number of occ after cleaning

for( i in 1:length(list_occ_vec)){ #Cleaning unit_points files
  Tag<-list_occ_vec[i]
  unit_points2<-Occ_used_for_SDM[Occ_used_for_SDM$Tag==Tag, c("Occurrence", "x","y", "Tag") ] 
  
  list_occ$N.obs_envOtl[list_occ$code_unit==Tag]<-sum(Occ_used_for_SDM$Occurrence[Occ_used_for_SDM$Tag==Tag])
    save(unit_points2, file = paste0("../input_data/Species_data/Spatial_Points_Objects/occurrences_", Tag,".RData")) # Sauvegarde du nouvel objet spatial des P/A
}
###Pas de changement notable de modele type donc pas besoin d'update list_occ

Occ_used_for_SDM<-merge(Occ_used_for_SDM, list_occ[, c(3,9)], by.x="Tag", by.y="code_unit")


```


```{r}
# G?n?ration du tableau final des outliers

Outliers.final <- merge(x = Outliers.index, y =Occ_used_for_SDM, by = "ID_obs")

save(Outliers.final, file = "../input_data/occurences_df/Outliers_env/Outliers.final.RData")
saveRDS(Outliers.final, file = "../input_data/occurences_df/Outliers_env/Outliers.final.RDS")



save(list_mimicry, file ="../input_data/useful_vectors/list_mimicry.RData")
save(list_species, file="../input_data/useful_vectors//list_species.RData")
save(list_occ_vec, file="../input_data/useful_vectors//list_occ_vec.RData")

list_tag_outliers_env <- as.character(unique(Outliers.final$Tag.x))
save(list_tag_outliers_env, file = "../input_data/useful_vectors/list.tag.outliers_env.RData")

save(Occ_used_for_SDM, file ="../input_data/occurences_df/Occ_used_for_SDM.RData")

saveRDS(Occ_used_for_SDM, file ="../input_data/occurences_df/Occ_used_for_SDM.RDS")

save(list_occ, file ="../input_data/occurences_df/list_occ_wt_modeletype.RData")

saveRDS(list_occ, file ="../input_data/occurences_df/list_occ_wt_modeletype.RDS")
```



