---
title: "07_Pseudoabsence"
output: html_document
---

##### Script 07: Generates pseudoabsences #####

###################################################
#      Authors: Eddie Pérochon & Maël Doré        #
#      Contact: eddie.perochon@hotmail.com        #
###################################################


### Goals = 
# Generates sets of pseudoabsences (PsA) (3 for restricted modelling, 9 for full modelling) for each ssp.
# Nb of sets based on model type, based on number of occurrences available
# Pseudo-absences drawn randomly from other samples sites, with a weighting-distance scheme, and a minimum buffer around occurrences

### Inputs =

#Occurrence data rasterized for each subspecies
#Environmental stack of selected variables

###

### Outputs
  
  # Matrix of distances among sample sites
  # Table of sampling site coordinates
  # Spatial objects with occurrences and PsA coordinates
  # PsA table for each ssp to use in biomod2
  # PDF plot of probability distribution of selected PsA for each set, for each ssp
  # PDF map of PsA set for each ssp


###

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
###clean envi + packages
rm(list = ls())

library(ade4)
library(dplyr)
library(sf)
library(raster)
library(rgl)
library(FactoMineR)
library(factoextra)
library(stringr)
library(tidyr)
library(tidyverse)
library(foreach)
library(doParallel)
library(ggplot2)

```

```{r fonction pour regarder les levels}
Donlev<-function(x) {levels(factor(x))}

```

```{r}
#Load files
load("../input_data/occurences_df/Occ_used_for_SDM.RData") #DF
load(file = "../input_data/occurences_df/list_occ_vec.RData") #vec for each ssp
load(file = "../input_data/occurences_df/list_occ_wt_modeletype.RData")# DF for each ssp
load(file = "../input_data/useful_vectors/list_species.RData")#vec for each sp
load(file = "../input_data/useful_vectors/list_mimicry.RData")#vec for each MR
load(file = "../input_data/useful_vectors/list.tag.outliers_env.RData")#vec for each env outlier

load(file = "../input_data/envData/Envstack.RData") #stack of envi var

if(length(list_occ$Sp_ID)==0){
list_occ<-base::merge(list_occ, Occ_used_for_SDM[,c("Tag", "Sp_ID")], by.x="code_unit", by.y="Tag", all.y=FALSE, no.dups=TRUE)
list_occ<-unique(list_occ)
} #add Sp_ID column only if it does not already exists
save(list_occ ,file = "../input_data/occurences_df/list_occ_wt_modeletype.RData")
```

```{r}
#add env data for each var in the DF



for(i in 1 : nrow(Occ_used_for_SDM)){
  for( j in 1 : length(names(Var_stack_final))){
    
    Occ_used_for_SDM[i, paste0(names(Var_stack_final)[j]) ] <- Var_stack_final[[j]]@data@values[ cellFromXY( Var_stack_final, c(Occ_used_for_SDM$x[i],Occ_used_for_SDM$y[i])) ]
    
  }
  
}
  

```


```{r}
###extract each min and max valor
MinMaxEnv<-data.frame(bio1=numeric(), bio2=numeric(), bio12=numeric(), bio15=numeric(), elev=numeric(), forest=numeric())
begin<-which( colnames(Occ_used_for_SDM)=="bio1" )
  
  for(j in begin : ncol(Occ_used_for_SDM))
    {
    MinMaxEnv[1,j-begin+1]<-min(Occ_used_for_SDM[j], na.rm=T)
    MinMaxEnv[2,j-begin+1]<-max(Occ_used_for_SDM[j], na.rm=T)
    }
row.names(MinMaxEnv)<-c("min", "max")
```

```{r}
###Looking for environnemental data with no occurences (<minvar & >maxvar)
 Var_stack_OUT<-Var_stack_final

for (i in 1:length(names(Var_stack_final))){
  minVar<-( Var_stack_OUT[[i]] < MinMaxEnv[1,i]) #min
  maxVar<-( Var_stack_OUT[[i]] > MinMaxEnv[2,i]) #max
  Var_stack_OUT[[i]]<-(minVar+maxVar)
  names(Var_stack_OUT)<-names(Var_stack_final)
}
 
names(Var_stack_OUT)<-names(Var_stack_final)

jpeg(file="../input_data/envData/EnvData_with_no_occurences.jpeg", quality = 300)
plot(Var_stack_OUT)
title(main = "Environnemental data with no occurences and their location",  line = -12.5)
dev.off() #plot to save it

#not much env data not covered with occurence so no need to use it for pseudoabs draw
```



```{r}
occ.coords <- Occ_used_for_SDM[, c("x","y")] 


# Rasterization of occurrences
raster.occ_full <- rasterize(x = occ.coords, # Occurrence coordinates
                             y = Var_stack_final, # Env stack grid to apply
                             field = 1, # Value to store in the raster
                             fun = function(x, ...) mean(x)) # Apply mean to keep value = 1 in case of multiple occurrences in one pixel


raster.occ_full<-projectRaster(from=raster.occ_full, crs = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs +towgs84=0,0,0")) #projection in WGS to use distances mesures because Moll does not deal good with distances

mydf <- structure(list(longitude = c(Occ_used_for_SDM$x), latitude = c(Occ_used_for_SDM$y)), .Names = c("x", 
"y"), class = "data.frame", row.names = c(NA, -(nrow(Occ_used_for_SDM)))) #coordsfor sptransform

Occ_WGS<-spTransform( 
  SpatialPointsDataFrame(data = Occ_used_for_SDM, 
                         coords = mydf, 
                         proj4string = CRS("+proj=moll +lon_0=-79 +lat_0=6 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=km +no_defs")),
          CRSobj = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs +towgs84=0,0,0")) #transform df into WGS

occ.coords<- as.data.frame(Occ_used_for_SDM[,c("LonWGS", "LatWGS")])
#change the coords vector with the right CRS
names(occ.coords)<-c("x","y")

cell_indices <- vector(mode = "integer", length = nrow(occ.coords))
for (i in 1:nrow(occ.coords)) {
  cell_indices[i] <- cellFromXY(raster.occ_full, occ.coords[i,]) #get cell indices for each occurence
}

# Use ID from 1 to last instead of cell indices
sampling_ID <- as.factor(as.numeric(as.factor(cell_indices)))
# 4168 sampling sites
```



```{r}

# Get coordinates of pixels associated with each occurrence
xy <- foreach (i = seq_along(cell_indices), .combine = rbind) %do% {
  xyFromCell(raster.occ_full, cell_indices[i])
}
  
raster_infos <- as.tibble(cbind(cell_indices, sampling_ID, xy))
raster_info_to_integer <-raster_infos %>%
  rename(LatWGS=y,
         LonWGS=x,
         cell_indicesWGS=cell_indices,
         sampling_ID_WGS=sampling_ID
         )

# Store infos on occurrences on raster grid in df of occurrences

if (length(dplyr::intersect(names(Occ_used_for_SDM), names(raster_info_to_integer))) > 0) {
 Occ_used_for_SDM <- Occ_used_for_SDM%>% 
    dplyr::select(-names(raster_info_to_integer))
}
Occ_used_for_SDM <- Occ_used_for_SDM %>%
  bind_cols(raster_info_to_integer)

  save(Occ_used_for_SDM, file = "../input_data/occurences_df/Occ_used_for_SDM.RData")
  saveRDS(Occ_used_for_SDM, file = "../input_data/occurences_df/Occ_used_for_SDM.RDS")


### Generate table of sampling sites coordinates
sampling.sites_coords_with_index_and_cell_nb <- raster_infos %>% 
  unique() %>% 
  arrange(sampling_ID)


save(sampling.sites_coords_with_index_and_cell_nb, file = "../input_data/Sampling_sites/sampling.sites_coords_with_index_and_cell_nb.RData")

sampling.sites_coords <- sampling.sites_coords_with_index_and_cell_nb %>% 
  dplyr::select(x, y)

save(sampling.sites_coords, file = "../input_data/Sampling_sites/sampling.sites_coords.RData")


### Compute distance matrix of all sampling sites
Sampling.sites.Dist = geosphere::distm(x = sampling.sites_coords)/900 # Geometric distance on WGS84 ellipsoid, in km

save(Sampling.sites.Dist, file = "../input_data/Sampling_sites/Sampling.sites.Dist.RData")
```

```{r}
##### 2/ Get a record of sampling sites that do not have associated env. data to discard them from the potential PsA pool ####

load(file = "../input_data/Sampling_sites/sampling.sites_coords.RData")
envMW<-readRDS(file="../input_data/envData/Envstack.rds")


EnvWGS<-projectRaster(from=Var_stack_final, crs = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs +towgs84=0,0,0"))
sampling.sites_coords$env_data<-NA

    SSCMW<-sampling.sites_coords #get data 
    SSCMW$id<-1:nrow(SSCMW) #to keep row order
    SSCMW2<-merge(SSCMW, unique(Occ_used_for_SDM[,c("LonWGS","LatWGS","x","y")]), by.x=c("x","y"), by.y=c("LonWGS", "LatWGS")) #merge with original moll coords
    row.names(SSCMW2)<-SSCMW2$id
    SSCMW2<-SSCMW2[order(SSCMW2$id),] #original order
    SSCMW2=SSCMW2%>%
      rename (xWGS=x, yWGS=y, x=x.y, y=y.y)
    
for (i in 1:nrow(sampling.sites_coords)) {
  
  # Extract env values for each sampling sites
  test <- raster::extract(EnvWGS, sampling.sites_coords[i, 1:2])
  
  # If any env values is missing, note to not use this sampling site as potential PsA site
  sampling.sites_coords$env_data[i] <- all(!is.na(test))
}
    #########Get the same info for MW projection
    SSCMW2$env_data<-NA
for (i in 1:nrow(SSCMW2)) {
  
  # Extract env values for each sampling sites
  test <- raster::extract(envMW, SSCMW2[i, c("x","y")])
  
  # If any env values is missing, note to not use this sampling site as potential PsA site
  SSCMW2$env_data[i] <- all(!is.na(test))
} 

    ####add the WGS without envi to the list
for (i in 1:nrow(sampling.sites_coords)) {
  if(sampling.sites_coords$env_data[i]!=SSCMW2$env_data[i]){
    sampling.sites_coords$env_data[i]<-SSCMW2$env_data[i]
  }
  
}    
    

sum(!sampling.sites_coords$env_data) # 24 sampling sites out of 4168 are not available to draw PsA because they lack env data

save(sampling.sites_coords, file = "../input_data/Sampling_sites/sampling.sites_coords.RData")
save(EnvWGS, file= "../input_data/envData/Var_stack_WGS84.RData")
saveRDS(EnvWGS, file= "../input_data/envData/Var_stack_WGS84.RDS")

```

```{r}
##### 3/ Generate PA tables: Parallelized version #####

# Changes =

# Add library loading in the loop
# Modify lines that assign value in object outside of the loop : list.models
#    N.obs et dérivés
# Generate a return(list()) for these objects that are not saved at each iteration, typically infos you want to store in a vector/list/table for each iteration
# Add script to geenrate and close the cluster
# foreach ... %dopar%


# Remove environment
#rm(list = ls())

### 3.1/ Set up the cluster ####

#library(foreach)
#library(doParallel)

# Detect the number of threads
#numCores <- detectCores()
# registerDoParallel(numCores)  # To set the nb if threads to use when using %dopar%

#cl <- makeCluster(numCores) # Generate the virtual cluster from the number of threads
#registerDoParallel(cl)      # To set the virtual cluster when using %dopar%

# getDoParWorkers() # Pour vérifier le nombre de coeurs enregistrés

### 3.2/ Load stuff useful for all units (outside the loop) ####

### Load table to track model outputs
load(file = "../input_data/occurences_df/list_occ_wt_modeletype.RData")
load("../input_data/occurences_df/list_occ_vec.RData")
load("../input_data/useful_vectors/list_species.RData")

### Load occurrence dataset
  load(file = "../input_data/occurences_df/Occ_used_for_SDM.RData")

# Load environmental stack
envData <- readRDS(file = "../input_data/envData/Var_stack_WGS84.RDS")
envMW<-readRDS(file="../input_data/envData/Envstack.rds")

### Load sampling sites infos for PsA Generation
load(file = "../input_data/Sampling_sites/Sampling.sites.Dist.RData")
load(file = "../input_data/Sampling_sites/sampling.sites_coords.RData")

source("../functions/progcombine.R")

# Set seed to ensure repetability of random PsA draws
set.seed(277461)


### 3.3/ Loop to generate PsA table for each units/OMU ####
for(k in seq_along(list_occ_vec))
  {
#temp <- foreach (k = seq_along(list_occ_vec), .combine = progcombine_rbind(nreps = length(list_occ_vec)), .init = NULL) %dopar% {
# temp <- foreach (k = 1:5) %dopar% {
  # k <- 1
  
  unit <- as.character(list_occ_vec[k])
  ModeleType <- list_occ$initial_model_type[k]
  N.obs<-list_occ$N.obs_envOtl[k]
  
  ##### 3.3.1/ PsA generation ####
  
  ### Only for OMU/unit that will be modeled, to save time
  
  if (ModeleType =="rasterized") { 
    
    # Warning message for OMU with too low sample size to try a SDM
    cat(paste0(Sys.time(), " - No Pseudo-Absences Generation for ", unit, " = Unit N°",k,"\n"))
    
  } else { # PsA Generation for OMU with at least 6 obs.
    
    cat("\n", as.character(Sys.time()), "----- PsA generation starts for", unit, "= Unit N°",k,"\n")
    
    # Load occurrences coordiantes and spatial object
    unit.occurrence <- Occ_used_for_SDM[Occ_used_for_SDM$Tag == unit, c("LonWGS","LatWGS")]
    load(file = paste0("../input_data/Species_data/Spatial_Points_Objects/occurrences_", unit,".RData"))
    
     unit_points<- spTransform( 
  SpatialPointsDataFrame(data = unit_points2, 
                         coords = unit_points2[, c("x", "y")], 
                         proj4string = CRS("+proj=moll +lon_0=-79 +lat_0=6 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=km +no_defs")),
          CRSobj = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs +towgs84=0,0,0"))
    
    
    # Get species name for output paths
    sp <- list_occ$Sp_ID[k]
    
    # Retrieve sampling sites ID for this OMU
    unit_sampling_ID <- unique(Occ_used_for_SDM[Occ_used_for_SDM$Tag == unit, "sampling_ID_WGS"])
    
    # Extract the minimal distance of sampling sites, to any of the occurrence points of this OMU
    if (length(unit_points) == 1) { # Case with a simple occurrence point
      Closest.dist <- Sampling.sites.Dist[unit_sampling_ID,] 
    } else { # Case with multiple occurrence points
      Closest.dist <- apply(X = Sampling.sites.Dist[unit_sampling_ID,], MARGIN = 2, FUN = min)
    }
    
    # Select only sampling points outside the buffer zone to draw potential PsA
    # Also discard PsA that do not have env data associated with (because of small errors in GPS coordiantes for points lying close to coastlines)
    buffer <- 120 # Buffer = 4 cells
    index.potential.PsA <- which((Closest.dist > buffer) & sampling.sites_coords$env_data==TRUE)
    
    # Compute weights for probability of drawing a site
    weights <-  Closest.dist[index.potential.PsA]
    # weights <-  1/(weights*weights) # Weights are inversly proportionnal to the square of distance such as 1/d²
    weights <-  1/(weights) # Weights are inversly proportionnal to distance such as 1/d
    # weights <- (weights - min(weights)) / (max(weights) - min(weights)) # Normalise to 0 - 1 range
    
    # Generate temporary PA.table to store indices of sampling sites
    
    if (ModeleType=="restricted") {
      n.PsA.set <- 9 # 9 PsA for OMU with limited N.obs
    } else { 
      n.PsA.set <- 3  # 3 PsA sets for OMU with enough N.obs to do CV
    } 
    
    PA.indices.table <- data.frame(matrix(nrow = N.obs, ncol = n.PsA.set))
    for (i in 1:n.PsA.set) {
      PA.indices.table[,i] <- sample(x = index.potential.PsA, size = N.obs, prob = weights, replace = F)
    }
    PA.list <- as.vector(as.matrix(PA.indices.table)) # Concatenate in a single vector all the indices of sample sites to use as PsA
    
    PA_set <- as.factor(as.vector(matrix(data = 1:n.PsA.set, byrow = T, nrow = N.obs, ncol = n.PsA.set))) # Generate a vector of PsA set attribution
    ggplot.table <- tibble("indices" = PA.list, "PA_set" = PA_set, "dist" = Closest.dist[PA.list], "weights" = 1/Closest.dist[PA.list])
    
    ### 3.3.2/ Plot probability distribution of selected PsA for each set ####
    
    pdf(file = paste0("../input_data/Species_data/Pseudo_absences/Proba_distri_PsA_",unit,".pdf"), height = 8, width = 8)
    g <- ggplot.table %>% 
      ggplot(aes(x = dist, y = weights, colour = PA_set)) +
      geom_point(size = 3, alpha = 0.5, fill = NA, position = position_jitter(width = max(ggplot.table$dist)/50, height = max(ggplot.table$weights)/50, seed = 5)) +
      guides(colour = guide_legend(override.aes = list(alpha = 1))) +
      labs(title = paste0("Probability distribution of PsA for ", unit),
           x = "Distance in km", y = "Weights")
    print(g)
    dev.off()  
    
    # Copy in the sp folder
    file.copy(from = paste0("../input_data/Species_data*/Pseudo_absences/Proba_distri_PsA_",unit,".pdf"), to = paste0("../maps/By_sp/",sp,"/Proba_distri_PsA_",unit,".pdf"), overwrite = T)
    
     ### 3.3.3/ Plot selected PsA of each set on a map ####
   unit_pointsMW<-spTransform(unit_points, CRSobj =CRS("+proj=moll +lon_0=-79 +lat_0=6 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=km +no_defs") ) ##Back to MW for mapping
  
    
        
    ###########Problem with moll proj so need to get the original x y set 
    SSCMW<-sampling.sites_coords #get data 
    SSCMW$id<-1:nrow(SSCMW) #to keep row order
    SSCMW2<-merge(SSCMW, unique(Occ_used_for_SDM[,c("LonWGS","LatWGS","x","y")]), by.x=c("x","y"), by.y=c("LonWGS", "LatWGS")) #merge with original moll coords
    row.names(SSCMW2)<-SSCMW2$id
    SSCMW2<-SSCMW2[order(SSCMW2$id),] #original order
    SSCMW2=SSCMW2%>%
      rename (xWGS=x, yWGS=y, x=x.y, y=y.y)
    
      
    sampling.sites_coordsMW<- SpatialPointsDataFrame(data = SSCMW2,
                         coords = sampling.sites_coords[, c("x", "y")], 
                         proj4string =  CRS("+proj=moll +lon_0=-79 +lat_0=6 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=km +no_defs"))

    
    
    pdf(file = paste0("../input_data/Species_data/Pseudo_absences/PsA_map_",unit,".pdf"), height = 8, width = 8) 
    plot(Var_stack_final[["elev"]], main = unit)
    for (i in 1:n.PsA.set) {
      points(sampling.sites_coordsMW[PA.indices.table[,i], 1:2], col = c("red","darkgreen","blue", "gold","cyan","limegreen","purple","grey","orange","deeppink")[i], pch = 1, cex = 0.7)
      points(unit_pointsMW, col = "red", cex = 1.1, pch = 16)
      points(unit_pointsMW, cex = 1, pch = 16)
    }
    legend(legend = c("Presences",paste0(rep("PA",n.PsA.set),1:n.PsA.set)), pch = c(16, rep(1,n.PsA.set)), 
           col = c("black","red","darkgreen", "blue","gold","cyan","limegreen","purple","grey","orange","deeppink")[1:n.PsA.set],
           x = "bottomleft", pt.cex = 1, cex = 0.9, bty ="o")
    dev.off()
    
      # Copy in the sp folder for Maps
    file.copy(from =  paste0("../input_data/Species_data/Pseudo_absences/PsA_map_",unit,".pdf"), to = paste0("../Maps/By_sp/",sp,"/PsA_map_",unit,".jpeg"), overwrite = T)
    

       
    ### 3.3.4/ Retrieve coordinates of PsA and save in sp object ####
    Occ.coord <- unit_points@coords
    PsA.coord <- sampling.sites_coords[PA.list, 1:2]
    names(Occ.coord) <- names(PsA.coord) <- c("x", "y")
    All.coord <- rbind(Occ.coord,PsA.coord)
    
    # Append the spatial object for this unit, adding the PsA
    
    unit_points.PsA <- spTransform(SpatialPointsDataFrame(All.coord, # Coordinates of occurrences data and PsA
                                              data = data.frame(Presences_Pseudo.Absences = c(rep(x = 1, times = nrow(Occ.coord)), rep(x = NA, times = nrow(PsA.coord)))), # 1 = Presence point, NA = PsA
                                              proj4string = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs +towgs84=0,0,0")),
                                   CRSobj=CRS("+proj=moll +lon_0=-79 +lat_0=6 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=km +no_defs"))# Define CRS
    
    
    
    save(unit_points.PsA, file = paste0("../input_data/Species_data/Spatial_Points_Objects/occ_&_PsA_", unit,".RData"))
    saveRDS(unit_points.PsA, file = paste0("../input_data/Species_data/Spatial_Points_Objects/occ_&_PsA_", unit,".rds"))
    
     
   
    ### 3.3.5/ Generate the associated PA.table for Biomod2 ####
    
    # Fill a df with F value. One row = one occurrence or PsA. One column = One PSA run
    PA.table <- data.frame(matrix(data = F, nrow = N.obs*(n.PsA.set+1), ncol = n.PsA.set))
    
    # Fill occurrences point rows with T
    PA.table[1:N.obs,] <- T # All presences need to be taken at all time
    
    # Fill PsA point rows with T, only for their PsA run
    for (i in 1:n.PsA.set) {
      PA.table[(N.obs+((i-1)*N.obs)+1):(N.obs+(i*N.obs)), i] <- T # Take only the 9 PsA associated with the random sampling
    }
    
    names(PA.table) <- paste0("PA", 1:n.PsA.set)
    
    save(PA.table, file = paste0("../input_data/Species_data/PA.Tables/PA.table_", unit,".RData"))
    saveRDS(PA.table, file = paste0("../input_data/Species_data/PA.Tables/PA.table_", unit,".rds"))
    
    cat(paste0(Sys.time(), " - Pseudo-Absences Generation for ", unit, " = Unit N°",k," - Done\n"))
    
  }
  
}

# Close clusters generated with registerDoParallel(numCores)
 stopImplicitCluster()
# Close clusters generated with makeCluster 
#stopCluster() 

```


