---
title: "17_Merging_Species"
author: "Eddie Pérochon"
date: "10/05/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##### Script 17 : Merging species #####

###################################################
#      Authors: Eddie Pérochon & Maël Doré        #
#      Contact: eddie.perochon@hotmail.com        #
###################################################


### Goals = 
# Create maps at species level by computing "probability" of presence of any of the ssp of the species
# Generate a continuous map for each 4 option between Jaccard/TSS and Buffer.80/95

 
### Inputs 
   # Stack of continuous EM and binary maps for each ssp, per species from script 11
###

### Outputs
   # Species continuous map for each 4 option between Jaccard/TSS and Buffer.80/95
   # Summary of composition of species stack: with/without rasterized ssp, only rasterized ssp
###



```{r}
# Effacer l'environnement
rm(list = ls())

library(raster)
library(dplyr)
```

```{r}

# Load Summary table for unit and Species vector
load(file = paste0("../input_data/occurences_df/list_occ_after_clipping.RData"))
 
load(file="../input_data/useful_vectors/list_species.RData")

# Make a list of modeled and non-modeled units (occ.unit = with only occurrences points)
modeled_ssp <- list_occ[!is.na(list_occ$Model_ID), ]
rasterized_ssp <- list_occ[is.na(list_occ$Model_ID), ]

# Function to compute probability of presence with multiple OMUs
aggreg_prob = function(x, na.rm) { 
  y <- 1-prod(1-x) # Probability of presence of species = probability of presence of at least one OMU = opposite of probability of absence of all OMU
  return(y) # Output
}

list_occ$one.Binaries_sp <- F # To record which species include at least one binaries maps
list_occ$all.Binaries_sp <- F # To record which species include only binaries maps

continent_mask <- readRDS("../input_data/envData/continent_mask.RDS")
```

```{r}
### Loop by species
p<-progress_estimated(length(list_species), min_time=10)

for (i in 1:length(list_species)) 
{
   p$pause(0.1)$tick()$print()
  # i <- 23
  
  # Load a random layer to initiate the stacks (to remove later)
  sp.stack_Jaccard.80 <- sp.stack_Jaccard.95 <- sp.stack_TSS.80 <- sp.stack_TSS.95 <- stack(continent_mask) 
  
  # Load Species name
  sp <- as.character(list_species[i]) 
  
  # Create directory to store outputs per species
  if(!dir.exists(paste0("../outputs/By_species/",sp))) { # Test if the folder exists already or not
    dir.create(paste0("../outputs/By_species/",sp), recursive = T) # Create folder if absent
  }
  
  # Create directory to store maps per species
  if(!dir.exists(paste0("../Maps/By_species/",sp))) { # Test if the folder exists already or not
    dir.create(paste0("../Maps/By_species/",sp), recursive = T) # Create folder if absent
  }
  
  ssp_list <- modeled_ssp[modeled_ssp$Sp_ID == sp, ]
  if (nrow(ssp_list) > 0) {      # If at least one OMU was modeled
    
    for (j in 1:nrow(ssp_list))  # For each OMU
    { 
      unit <-  as.character(ssp_list$biomodTag[j]) # Load the unit name                  
      
      # Jaccard.80: Load the continuous maps and stack them all
      Ensemble_Jaccard_median_cropped_80 <- readRDS(file = paste0("../outputs/By_unit/",unit,"/Ensemble_Jaccard_median_cropped_80.rds"))
      sp.stack_Jaccard.80 <- addLayer(sp.stack_Jaccard.80, Ensemble_Jaccard_median_cropped_80)

      # Jaccard.95: Load the continuous maps and stack them all
      Ensemble_Jaccard_median_cropped_95 <- readRDS(file = paste0("../outputs/By_unit/",unit,"/Ensemble_Jaccard_median_cropped_95.rds"))
      sp.stack_Jaccard.95 <- addLayer(sp.stack_Jaccard.95, Ensemble_Jaccard_median_cropped_95)
      
      # TSS.80: Load the continuous maps and stack them all
      Ensemble_TSS_median_cropped_80 <- readRDS(file = paste0("../outputs/By_unit/",unit,"/Ensemble_TSS_median_cropped_80.rds")) 
      sp.stack_TSS.80 <- addLayer(sp.stack_TSS.80, Ensemble_TSS_median_cropped_80)   
      
      # TSS.95: Load the continuous maps and stack them all
      Ensemble_TSS_median_cropped_95 <- readRDS(file = paste0("../outputs/By_unit/",unit,"/Ensemble_TSS_median_cropped_95.rds")) 
      sp.stack_TSS.95 <- addLayer(sp.stack_TSS.95, Ensemble_TSS_median_cropped_95)
    }
  }
  
  Binaries <- rasterized_ssp[rasterized_ssp$Sp_ID == sp,]
  if (nrow(Binaries) > 0) {  # If at least one OMU was rasterized
    
    list_occ$one.Binaries_sp[list_occ$Sp_ID == sp] <- T
    
    for (j in 1:nrow(Binaries)) {  # For each  OMU
      
      unit <-  as.character(Binaries$biomodTag[j]) # Load the unit name 
      
      # Create directory to store outputs per OMU
      if(!dir.exists(paste0("../outputs/By_unit/",unit))) { # Test if the folder exists already or not
        dir.create(paste0("../outputs/By_unit/",unit), recursive = T) # Create folder if absent
      }
      
      # Create directory to store maps per OMU
      if(!dir.exists(paste0("../maps/By_unit/",unit))) { # Test if the folder exists already or not
        dir.create(paste0("../maps/By_unit/",unit), recursive = T) # Create folder if absent
      }
      
      # # Load the rasterized occurrence map
      # Raster_Occ <- readRDS(file = paste0("../input_data/Species_data/",res,"/Binary_Rasters_from_Occurrences/",unit,".rds"))
      # 
      # # Add the continental borders as 0 values for empty pixels (oceans are NA)
      # rasterized_map <- continent_mask
      # rasterized_map[!is.na(Raster_Occ[])] <- 1
      # 
      # save(rasterized_map, file = paste0("../outputs/By_unit/",unit,"/rasterized_map_",unit,".RData"), version = "2")
      # saveRDS(rasterized_map, file = paste0("../outputs/By_unit/",unit,"/rasterized_map_",unit,".rds"), version = "2")
      # 
      # pdf(file = paste0("../maps/By_unit/",unit,"/rasterized_map_",unit,".pdf"), height = 6, width = 7)
      # plot(rasterized_map, main = unit)
      # dev.off()
      # # Copy in sp folder
      # file.copy(from = paste0("../maps/By_unit/",unit,"/rasterized_map_",unit,".pdf"), to = paste0("../maps/By_species/",sp,"/rasterized_map_",unit,".pdf"), overwrite = T)
      
      # Load the rasterized map, with continental borders
      load(file = paste0("../outputs/By_unit/",unit,"/raster_stack_cropped.RData"))
      rasterized_map <- Select_raster_stack_cropped
      # Jaccard.80: Load the binary maps and stack them all
      sp.stack_Jaccard.80 <- addLayer(sp.stack_Jaccard.80, rasterized_map)

      # Jaccard.95: Load the binary maps and stack them all
      sp.stack_Jaccard.95 <- addLayer(sp.stack_Jaccard.95, rasterized_map)
      
      # TSS.80: Load the binary maps and stack them all
      sp.stack_TSS.80 <- addLayer(sp.stack_TSS.80, rasterized_map)   
      
      # TSS.95: Load the binary maps and stack them all
      sp.stack_TSS.95 <- addLayer(sp.stack_TSS.95, rasterized_map)
      
    }
  }
  
  # Note case with only rasterized OMU
  if ((nrow(Binaries) > 0) & (nrow(ssp_list) == 0)) {
    list_occ$all.Binaries_sp[list_occ$Sp_ID == sp] <- T
  }
  
  # Drop the useless first layer used to initiate the stack
  sp.stack_Jaccard.80 <- dropLayer(sp.stack_Jaccard.80, i = 1)
  sp.stack_Jaccard.95 <- dropLayer(sp.stack_Jaccard.95, i = 1)
  sp.stack_TSS.80 <- dropLayer(sp.stack_TSS.80, i = 1)
  sp.stack_TSS.95 <- dropLayer(sp.stack_TSS.95, i = 1)
  
  # Compute probability map per Species
  
  sp.cont_Jaccard.80 <- calc(sp.stack_Jaccard.80, fun = aggreg_prob)
  sp.cont_Jaccard.95 <- calc(sp.stack_Jaccard.95, fun = aggreg_prob)
  sp.cont_TSS.80 <- calc(sp.stack_TSS.80, fun = aggreg_prob)
  sp.cont_TSS.95 <- calc(sp.stack_TSS.95, fun = aggreg_prob)
  
  plot(sp.cont_TSS.95)
  
  # Make sure to save the data, not just the link to the temp file!
  sp.cont_Jaccard.80 <- readAll(sp.cont_Jaccard.80)
  sp.cont_Jaccard.95 <- readAll(sp.cont_Jaccard.95)
  sp.cont_TSS.80 <- readAll(sp.cont_TSS.80)
  sp.cont_TSS.95 <- readAll(sp.cont_TSS.95)
  
  save(sp.cont_Jaccard.80, file = paste0("../outputs/By_species/",sp,"/cont_Jaccard.80_",sp,".RData"), version = "2")
  saveRDS(sp.cont_Jaccard.80, file = paste0("../outputs/By_species/",sp,"/cont_Jaccard.80_",sp,".rds"), version = "2")
  save(sp.cont_Jaccard.95, file = paste0("../outputs/By_species/",sp,"/cont_Jaccard.95_",sp,".RData"), version = "2")
  saveRDS(sp.cont_Jaccard.95, file = paste0("../outputs/By_species/",sp,"/cont_Jaccard.95_",sp,".rds"), version = "2")
  save(sp.cont_TSS.80, file = paste0("../outputs/By_species/",sp,"/cont_TSS.80_",sp,".RData"), version = "2")
  saveRDS(sp.cont_TSS.80, file = paste0("../outputs/By_species/",sp,"/cont_TSS.80_",sp,".rds"), version = "2")
  save(sp.cont_TSS.95, file = paste0("../outputs/By_species/",sp,"/cont_TSS.95_",sp,".RData"), version = "2")
  saveRDS(sp.cont_TSS.95, file = paste0("../outputs/By_species/",sp,"/cont_TSS.95_",sp,".rds"), version = "2")
  
  pdf(file = paste0("../Maps/By_species/",sp,"/cont_Jaccard.80_",sp,".pdf"), height = 6, width = 7)
  plot(sp.cont_Jaccard.80, main = sp)
  dev.off()

  pdf(file = paste0("../Maps/By_species/",sp,"/cont_Jaccard.95_",sp,".pdf"), height = 6, width = 7)
  plot(sp.cont_Jaccard.95, main = sp)
  dev.off()
  
  pdf(file = paste0("../Maps/By_species/",sp,"/cont_TSS.80_",sp,".pdf"), height = 6, width = 7)
  plot(sp.cont_TSS.80, main = sp)
  dev.off()
  
  pdf(file = paste0("../Maps/By_species/",sp,"/cont_TSS.95_",sp,".pdf"), height = 6, width = 7)
  plot(sp.cont_TSS.95, main = sp)
  dev.off()
  
  
}

```


```{r}
sum(list_occ$one.Binaries_sp) #  species among the  have at least one binary map used
sum(list_occ$all.Binaries_sp) #  species among the  are just modeled under binary maps

```

```{r}
##### Generate stack of all sps outputs for all options


All_sp_proba_stack_Jaccard.80 <- All_sp_proba_stack_Jaccard.95 <- All_sp_proba_stack_TSS.80 <- All_sp_proba_stack_TSS.95  <- stack(continent_mask) # 1e temp layer used to initiate stack, to remove afterwards
# i <- 1

p<-progress_estimated(length(list_species), min_time=10)
for (i in 1:length(list_species)) # By sp
{ 
  p$pause(0.1)$tick()$print()
  # Load sp name
  sp <- as.character(list_species[i])

  
  # Load Sp continuous probability map 
  sp.cont_Jaccard.80 <- readRDS(file = paste0("../outputs/By_species/",sp,"/cont_Jaccard.80_",sp,".rds"))
  sp.cont_Jaccard.95 <- readRDS(file = paste0("../outputs/By_species/",sp,"/cont_Jaccard.95_",sp,".rds"))
  sp.cont_TSS.80 <- readRDS(file = paste0("../outputs/By_species/",sp,"/cont_TSS.80_",sp,".rds"))
  sp.cont_TSS.95 <- readRDS(file = paste0("../outputs/By_species/",sp,"/cont_TSS.95_",sp,".rds"))
  
  # Build stack
  All_sp_proba_stack_Jaccard.80 <- addLayer(All_sp_proba_stack_Jaccard.80, sp.cont_Jaccard.80)
  All_sp_proba_stack_Jaccard.95 <- addLayer(All_sp_proba_stack_Jaccard.95, sp.cont_Jaccard.95)
  All_sp_proba_stack_TSS.80 <- addLayer(All_sp_proba_stack_TSS.80, sp.cont_TSS.80)
  All_sp_proba_stack_TSS.95 <- addLayer(All_sp_proba_stack_TSS.95, sp.cont_TSS.95)
  

}

# Drop the useless first layer used to initiate the stack
All_sp_proba_stack_Jaccard.80 <- dropLayer(All_sp_proba_stack_Jaccard.80, i = 1)
All_sp_proba_stack_Jaccard.95 <- dropLayer(All_sp_proba_stack_Jaccard.95, i = 1)
All_sp_proba_stack_TSS.80 <- dropLayer(All_sp_proba_stack_TSS.80, i = 1)
All_sp_proba_stack_TSS.95 <- dropLayer(All_sp_proba_stack_TSS.95, i = 1)

# Name layers with sp names
names(All_sp_proba_stack_Jaccard.80) <- names(All_sp_proba_stack_Jaccard.95) <- names(All_sp_proba_stack_TSS.80) <- names(All_sp_proba_stack_TSS.95)<- list_species

# nlayers(All_sp_proba_stack_Jaccard.95) # 388 species in the final stack

# Make sure to save the data, not just the link to the temp file!
All_sp_proba_stack_Jaccard.80 <- readAll(All_sp_proba_stack_Jaccard.80)
All_sp_proba_stack_Jaccard.95 <- readAll(All_sp_proba_stack_Jaccard.95)
All_sp_proba_stack_TSS.80 <- readAll(All_sp_proba_stack_TSS.80)
All_sp_proba_stack_TSS.95 <- readAll(All_sp_proba_stack_TSS.95)

# Save stacks
save(All_sp_proba_stack_Jaccard.80, file = paste0("../outputs/Indices_stacks/All_sp_proba_stack_Jaccard.80.RData"), version = "2")
saveRDS(All_sp_proba_stack_Jaccard.80, file = paste0("../outputs/Indices_stacks/All_sp_proba_stack_Jaccard.80.rds"), version = "2")
save(All_sp_proba_stack_Jaccard.95, file = paste0("../outputs/Indices_stacks/All_sp_proba_stack_Jaccard.95.RData"), version = "2")
saveRDS(All_sp_proba_stack_Jaccard.95, file = paste0("../outputs/Indices_stacks/All_sp_proba_stack_Jaccard.95.rds"), version = "2")
save(All_sp_proba_stack_TSS.80, file = paste0("../outputs/Indices_stacks/All_sp_proba_stack_TSS.80.RData"), version = "2")
saveRDS(All_sp_proba_stack_TSS.80, file = paste0("../outputs/Indices_stacks/All_sp_proba_stack_TSS.80.rds"), version = "2")
save(All_sp_proba_stack_TSS.95, file = paste0("../outputs/Indices_stacks/All_sp_proba_stack_TSS.95.RData"), version = "2")
saveRDS(All_sp_proba_stack_TSS.95, file = paste0("../outputs/Indices_stacks/All_sp_proba_stack_TSS.95.rds"), version = "2")

### Load directly the complete stack
All_sp_proba_stack_Jaccard.80 <- readRDS(file = paste0("../outputs/Indices_stacks/All_sp_proba_stack_Jaccard.80.rds"))
All_sp_proba_stack_Jaccard.95 <- readRDS(file = paste0("../outputs/Indices_stacks/All_sp_proba_stack_Jaccard.95.rds"))
All_sp_proba_stack_TSS.80 <- readRDS(file = paste0("../outputs/Indices_stacks/All_sp_proba_stack_TSS.80.rds"))
All_sp_proba_stack_TSS.95 <- readRDS(file = paste0("../outputs/Indices_stacks/All_sp_proba_stack_TSS.95.rds"))  

  

```

