---
title: "22_Bray_curtis_cooc"
author: "Eddie Pérochon"
date: "01/06/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


##### Script 22: Bray Curtis index #####

###################################################
#      Authors: Eddie Pérochon & Maël Doré        #
#      Contact: eddie.perochon@hotmail.com        #
###################################################


### Goals = 
##### Community structure with Bray-Curtis indices on comimetic pairs of ssps & OMUs #####

# Compute BC indices for all ssps & OMUs
# Compute mean BC for mimics only and non-mimics only
# Compute mean BC per mimicry rings
# Generate null distribution with randomization of mimicry patterns
# Plot test results


### Inputs 
# Inputs
# Summary table of ssps & OMUs
# Stack of ssps & OMUs probabilities of presence

###

### Outputs

# Matrix of probabilities of presence for ssps & OMUs x communities
# BC indices for all pairs of ssps, only comimics, only non-comimics, and per rings, and associated means
# Null distribution of mean values
# Plot of null distribution and test for all rings, and per rings
# Summary table for each ring of BC values

# Final plot with null distri for Ist and mean BC for comimics

###





```{r}
rm(list = ls())

library(raster)
library(vegan)
library(ggplot2)
library(dplyr)
library(stringr)
```

```{r}
### 1/ Load stuff ####

# Load summary table for unit & omu list
load(file = paste0("../input_data/occurences_df/list_occ_after_clipping_rs.RData"))
list_occ <- list_occ[!is.na(list_occ$MR_ss),]
# load(file = "../input_data/occurences_df/list_OMU.RData")



load(file="../input_data/envData/continent_mask.RData")

# Load OMU/unit probability stack

# # list_OMU$OMU2<-str_replace_all( list_OMU$OMU, c("DENNIS.RAY"="DENNIS-RAY", "HALF.DENNIS"="HALF-DENNIS", "ST.ANDREW"="ST ANDREW", "POSTMAN.REVERSE"="POSTMAN REVERSE", "BLUE.MASK"="BLUE MASK", "RED.BAND"="RED BAND") )
# save(list_OMU, file="../input_data/occurences_df/list_OMU.RData")

for(m in c("ss", "sl"))
# for(m in c("ss"))
{
  OMU_proba_stack<-continent_mask
  list_OMU <- unique(list_occ[, paste0("OMU_",m)])
  
for(i in 1:length(list_OMU))
{
  
OMU<-list_OMU[i]
  
OMU_layer<-readRDS(file = paste0("../outputs/By_OMU/",OMU,"/cont_Jaccard.80_",OMU,".RDS"))
OMU_proba_stack <- stack(OMU_proba_stack, OMU_layer)

if (i %% 10 == 0) {print(i)}
}
OMU_proba_stack<-dropLayer(OMU_proba_stack, 1)
names(OMU_proba_stack)<-list_OMU

save(OMU_proba_stack, file=paste0("../input_data/Species_data/OMU_proba_stack_",m,".RData"))
saveRDS(OMU_proba_stack, file=paste0("../input_data/Species_data/OMU_proba_stack_",m,".RDS"))
##Load ssp proba stack

ssp_proba_stack<-continent_mask

for(i in 1:nrow(list_occ))
{
  
  ssp<-list_occ$biomodTag[i]
if(list_occ$initial_model_type[i]=="rasterized")
{
load(file = paste0("../outputs/By_unit/",ssp,"/raster_stack_cropped.RData"))
  ssp_layer<-Select_raster_stack_cropped
}
  else {
    ssp_layer<-readRDS(paste0("../outputs/By_unit/",ssp,"/all_EM_Jaccard_buffer_80.RDS"))[[1]]
  }
ssp_proba_stack <- stack(ssp_proba_stack, ssp_layer)
if (i %% 10 == 0) {print(i)}
}
ssp_proba_stack<-dropLayer(ssp_proba_stack, 1)
names(ssp_proba_stack)<-list_occ$biomodTag
save(ssp_proba_stack, file="../input_data/Species_data/ssp_proba_stack.RData")
saveRDS(ssp_proba_stack, file="../input_data/Species_data/ssp_proba_stack.RDS")


### 2/ Generate matrix communities * OMU for probabilities of presence ####
OMU_proba_brick <- readAll(OMU_proba_stack*1)
com_unit_mat <- NA
for (i in 1:nlayers(OMU_proba_brick)) 
{
  if (i==1){
    com_unit_mat <- OMU_proba_brick[[i]]@data@values
  }else{
    unit.values <- OMU_proba_brick[[i]]@data@values
    com_unit_mat<- cbind(com_unit_mat, unit.values)
  }
  if (i %% 10 == 0) {print(i)}
}
names(com_unit_mat) <- names(OMU_proba_brick)
rm(OMU_proba_brick)


ssp_proba_brick <- readAll(ssp_proba_stack*1)
com_ssp_mat <- NA
for (i in 1:nlayers(ssp_proba_brick)) 
{
  if (i==1){
    com_ssp_mat <- ssp_proba_brick[[i]]@data@values
  }else{
    unit.values <- ssp_proba_brick[[i]]@data@values
    com_ssp_mat<- cbind(com_ssp_mat, unit.values)
  }
  if (i %% 10 == 0) {print(i)}
}
names(com_ssp_mat) <- names(ssp_proba_brick)
rm(ssp_proba_brick)

saveRDS(com_unit_mat, file = paste0( "../input_data/com_unit_mat_",m,".rds"))
saveRDS(com_ssp_mat, file =paste0("../input_data/com_ssp_mat_",m,".rds"))


# Filter out communities with NA
real_com_index <- NA
for (j in 1:2) {
  if(j==1)
  {mod=com_unit_mat
  modname="com_unit_mat"}
  else {mod=com_ssp_mat
  modname="com_ssp_mat"}

for (i in 1:nrow(mod)) 
{
  com.row <- mod[i,]
  real_com_index[i] <- (!any(is.na(com.row)))&(!any(is.nan(com.row)))
}
  
Filtered_com <- mod[real_com_index,]
nrow(Filtered_com) # 30555 community with no NA
if(j == 2)
{
saveRDS(Filtered_com, file = paste0("../input_data/SDM_stacks/Filtered",modname,".rds"))
}

if(j == 1)
{
  saveRDS(Filtered_com, file = paste0("../input_data/SDM_stacks/Filtered",modname,"_",m,".rds"))
}
}

# Load directly the matrix of community * units probability presence
com_unit_mat <- readRDS(file = paste0("../input_data/SDM_stacks/Filteredcom_unit_mat_",m,".rds"))
com_ssp_mat <- readRDS(file = paste0("../input_data/SDM_stacks/Filteredcom_ssp_mat.rds"))

### 3/ Compute Bray-Curtis indices ####

### 3.1/ Compute Bray-Curtis index for all pairs of units ####
library(vegan)
# names(list_OMU)<-c("biomodTag","Ring","", "OMU2")
# 
# list_occ$Ring<-str_replace_all( list_occ$Mimicry_ring, c("DENNIS-RAY"="DENNIS.RAY", "HALF-DENNIS"="HALF.DENNIS", "ST ANDREW"="ST.ANDREW", "POSTMAN REVERSE"="POSTMAN.REVERSE", "BLUE MASK"="BLUE.MASK", "RED BAND"="RED.BAND") )

v=colSums(com_ssp_mat)==0 #5 suspecies with small distrib have 0, cant manage to find why

for (k in 1:2) {
  if(k==1)
  {mod=com_unit_mat
  modname="com_unit_mat"
  typename="OMU"
  list_type=list_OMU}
  else {mod=com_ssp_mat[, v==FALSE]
  modname="com_ssp_mat"
  typename="ssp"
  list_type=list_occ[v==FALSE,]}

dim(mod)
unit_BC_dist <- vegdist(x = t(mod), method = "bray") # Compute dissimilarities between rows

saveRDS(unit_BC_dist, file = paste0("../outputs/Community_Structure/",typename,"_BC_dist_",m,".rds"))
save(unit_BC_dist, file =paste0("../outputs/Community_Structure/",typename,"_BC_dist_",m,".RData"))

# Load directly the vector of BD distances among all units
unit_BC_dist <- readRDS(file = paste0("../outputs/Community_Structure/",typename,"_BC_dist_",m,".rds"))

stack_name <-  paste0("../input_data/Species_data/",typename,"_proba_stack.RDS")
if(typename == "OMU")
{
  stack_name <-  paste0("../input_data/Species_data/",typename,"_proba_stack_",m,".RDS")
}

unit_proba_stack <- readRDS(file = stack_name)

if(typename=="ssp")
{
unit_proba_stack<- subset(unit_proba_stack, which(v==FALSE))
tag <- "biomodTag"
} else {
 tag <-  paste0("OMU_",m)
}
# hist(unit_BC_dist)

unit_BC_dist_mat <- as.matrix(unit_BC_dist)

mimicry.list <- as.character(unique(list_occ[,paste0("MR_", m)]))



### 3.2/ Compute mean BC per mimicry rings ####
mean_BC <- NA
for (i in 1:length(mimicry.list)) # Per mimicry rings
{ 
  ring <- mimicry.list[i]
  
  # Get names and indices of all units/OMUs for this ring
  tags <- as.character(list_occ[,tag][list_occ[,paste0("MR_",m)] == ring]) # Get names of all OMUs in the ring
  tags <- unique(tags[tags %in% names(unit_proba_stack)])
  
  index <- which(names(unit_proba_stack) %in% tags) # Get index of layer for these OMUs
  index
  
  
  if (length(tags) == 1) # Case with only one OMU in the mimicry ring. Impossible to compute pairwise distances
  {
    mat.index <- data.frame(matrix(nrow = 2, ncol = 0)) # Empty df of pairs indices (no pairs of OMUs)
    save(mat.index, file = paste0("../outputs/Community_Structure/BC_mimicry_ring_mat/mat.index.",ring,"_",typename,"_",m,".RData"))
    BC <- c() # Empty vector of Bray-Curtis values
    save(BC, file = paste0("../outputs/Community_Structure/BC_mimicry_ring_mat/BC.",ring,"_",typename,"_",m,".RData"))
    mean_BC[i] <- NA
  } else { # Case with at least 2 OMUs.
    mat.index <- combn(x = index, m = 2, FUN = c) # Get all combinations possibles for pairs of OMUs indices
    save(mat.index, file = paste0("../outputs/Community_Structure/BC_mimicry_ring_mat/mat.index.",ring,"_",typename,"_",m,".RData"))
    BC <- c(rep(1, ncol(mat.index))) # Initiate the vector used to store all BC values
    for (j in 1:ncol(mat.index)) # For each pair of OMUs
    {
      BC[j] <- unit_BC_dist_mat[mat.index[1,j], mat.index[2,j]] # Extract Bray-Curtis index from the complete matrix of BC indices
    }
    save(BC, file = paste0("../outputs/Community_Structure/BC_mimicry_ring_mat/BC.",ring,"_",typename,"_",m,".RData")) # Save the vector of BC for all pairs of OMUs in this ring
    mean_BC[i]  <- mean(BC) # Compute mean BC for all pairs of this mimicry ring and store it in final vector
  }
  
  cat(paste0(Sys.time(), " - ", ring," - n°",i, " on ",length(mimicry.list),"\n"))
  
}
names(mean_BC) <- mimicry.list # Associate mean BC value with ring name
save(mean_BC, file = paste0("../outputs/Community_Structure/mean_BC_",typename,"_",m,".RData")) # Save final vector with mean BC values per ring
saveRDS(mean_BC, file = paste0("../outputs/Community_Structure/mean_BC_",typename,"_",m,".rds")) # Save final vector with mean BC values per ring

# Load mean BC of mimicry rings
load(file = paste0("../outputs/Community_Structure/mean_BC_",typename,"_",m,".RData"))
mean_BC

### 3.3/ Compute mean BC for all comimics, all rings taken into account ####

# Retrieve all co-mimic coordinates

all_mimic_mat_index <- data.frame(matrix(ncol = 0, nrow=2)) # Generate empty df to store indices of pairs of comimics
for (i in 1:length(mimicry.list))  # Per mimetic ring
{ 
  ring <- mimicry.list[i]
  load(file = paste0("../outputs/Community_Structure/BC_mimicry_ring_mat/mat.index.",ring,"_",typename,"_",m,".RData")) # Load the matrix of indices of pairsof comimics for this ring
  all_mimic_mat_index <- cbind(all_mimic_mat_index,mat.index) # Merge them all in one df
}
dim(all_mimic_mat_index) # 14 659 pairs of co-mimic OMUs

save(all_mimic_mat_index, file = paste0("../outputs/Community_Structure/BC_mimicry_ring_mat/all_mimic_mat_index_",typename,"_",m,".RData"))
saveRDS(all_mimic_mat_index, file = paste0("../outputs/Community_Structure/BC_mimicry_ring_mat/all_mimic_mat_index_",typename,"_",m,".rds"))

# Retrieve all co-mimic BC values and non-co-mimic BC values at the same time
BC_mimic <- NA # Initiate final vector to store BC values for comimics
unit_BC_dist_mat_no_mimic <- unit_BC_dist_mat # Copy matrix of all BC indices for all pairs of OMUs
for (j in 1:ncol(all_mimic_mat_index)) # For all pairs of comimics
{
  BC_mimic[j] <- unlist(unit_BC_dist_mat[all_mimic_mat_index[1,j],all_mimic_mat_index[2,j]]) # Extract BC index for this pair of comimics
  unit_BC_dist_mat_no_mimic[all_mimic_mat_index[1,j],all_mimic_mat_index[2,j]] <- NA # Remove BC value of comimics from matrix of non-comimics pairs
  if (j %% 1000 == 0) {print(j)}
}
length(BC_mimic) # 14 659 pairs of co-mimic OMUs

save(BC_mimic, file = paste0("../outputs/Community_Structure/BC_mimic_",typename,"_",m,".RData")) # Save final vector with all BC values for comimics
saveRDS(BC_mimic, file = paste0("../outputs/Community_Structure/BC_mimic_",typename,"_",m,".rds")) # Save final vector with all BC values for comimics

# Retrieve all non-mimic BC values
BC_no_mimic <- unit_BC_dist_mat_no_mimic[upper.tri(unit_BC_dist_mat_no_mimic)] # Extract only one side of the triangle to avoid duplicate values of pairs
BC_no_mimic <- na.omit(BC_no_mimic) # Remove NA (the comimics pairs)
length(BC_no_mimic) # 291 494 pairs of non-mimic units

save(BC_no_mimic, file = paste0("../outputs/Community_Structure/BC_no_mimic_",typename,"_",m,".RData")) # Save final vector with all BC values for non-comimics
saveRDS(BC_no_mimic, file = paste0("../outputs/Community_Structure/BC_no_mimic_",typename,"_",m,".rds")) # Save final vector with all BC values for non-comimics


# Compute mean obs BC for each group
load(file = paste0("../outputs/Community_Structure/",typename,"_BC_dist_",m,".RData")) # All BC index (distance format)
load(file = paste0("../outputs/Community_Structure/BC_mimic_",typename,"_",m,".RData")) # Only mimic pairs (vector format)
load(file = paste0("../outputs/Community_Structure/BC_no_mimic_",typename,"_",m,".RData")) # Only non mimic pairs (vector format)

Global_mean_BC <- mean(unit_BC_dist) ; Global_mean_BC # 0.949
Global_mimic_mean_BC <- mean(BC_mimic) ; Global_mimic_mean_BC # 0.706
Global_no.mimic_mean_BC <- mean(BC_no_mimic) ; Global_no.mimic_mean_BC # 0.952

# Save all mean BC values for all pairs, only co-mimics, only non-comimics
save(Global_mean_BC, Global_mimic_mean_BC, Global_no.mimic_mean_BC, file =paste0( "../outputs/Community_Structure/All_Global_BC_",typename,"_",m,".RData"))

# Quick ugly boxplots
All_BC <- c(BC_mimic, BC_no_mimic)
Status <- as.factor(c(rep("Mimic", length(BC_mimic)), rep("Non-Mimic", length(BC_no_mimic))))
boxplot(All_BC ~ Status)

library(ggplot2)

boxplot_df <- data.frame(All_BC, Status, stringsAsFactors = T)
gg_boxplot <- ggplot(data = boxplot_df, aes(x = Status, y = All_BC)) +
  geom_violin() +
  coord_trans(y = "exp")
print(gg_boxplot)

# Histogram
# Plot distri of BC for mimic pairs
pdf(file = paste0("../outputs/Community_Structure/hist_BC_mimic_",typename,"_",m,".pdf"), height = 6.3, width = 6.5)
hist(BC_mimic, xlab = "Bray-Curtis index", main = "Bray-Curtis indices of comimic pairs")
abline(v = mean(BC_mimic), col = "red", lty = 2, lwd = 2)
legend(legend = c(paste0("Mean = ", round(mean(BC_mimic, na.rm = T),3)), 
                  paste0("CI 5% = ", round(quantile(BC_mimic, 0.05),3)),
                  paste0("CI 95% = ", round(quantile(BC_mimic, 0.95),3))),
       x = "topleft", cex = 1, bty ="n") 
dev.off()
}

##### 4/ Generate new virtual community matrices under null hypothesis of no effect of mimicry ring on OMUs presence ####
# analogous to DeVries et al.'s [1999] and Hill's [2010] test of mimicry structure across microhabitats

# Load directly the vector of BC distances among all units
for (l in 1:2) {
  if(l==1)
  {mod=com_unit_mat
  modname="com_unit_mat"
  typename="OMU"
  list_type=list_OMU}
  else {mod=com_ssp_mat[, v==FALSE]
  modname="com_ssp_mat"
  typename="ssp"
  list_type=list_occ[v==FALSE,]}



mimicry.list <- as.character(unique(list_occ[,paste0("MR_", m)]))

if(typename == "ssp")
{
  unit_BC_dist <- readRDS(file = paste0("../outputs/Community_Structure/",typename,"_BC_dist_",m,".rds"))
  unit_BC_dist_mat <- as.matrix(unit_BC_dist)
  OMU_proba_stack <- readRDS(file = paste0("../input_data/Species_data/",typename,"_proba_stack.RDS"))
  OMU_proba_stack<- subset(OMU_proba_stack, which(v==FALSE))
  tag <- "biomodTag"
} else{
  unit_BC_dist <- readRDS(file = paste0("../outputs/Community_Structure/",typename,"_BC_dist_",m,".rds"))
  unit_BC_dist_mat <- as.matrix(unit_BC_dist)
  tag <- paste0("OMU_", m)
  OMU_proba_stack <- readRDS(file = paste0("../input_data/Species_data/",typename,"_proba_stack_",m,".RDS"))
}
## Start the loop for permutations
BC_mimic_null <- BC_no_mimic_null <- NA # Create vectors to store simulated mean BC values for co-mimics and non-comimics
mean_BC_null <- matrix(ncol = length(mimicry.list), nrow = 0) # Create matrix to store mean simulated BC values for each mimicry ring for each simulation
 for (k in 1:999) # 999 simulations/permutations
# for (k in 382:999) 
{ 
  # k <- 1
  ## Suffle mimicry ring among units
  shuffle.list.unit <- list_occ
  shuffle.list.unit$Ring <- sample(as.character(list_occ[,paste0("MR_",m)]), replace = F)
  
  # # Check if number of unit per ring is preserved
  # table(list.unit$Mimicry.model)
  # table(shuffle.list.unit$Mimicry.model)
  
  ## Generate the new Mimicry rings Richness Stack with random attribution of OMUs to mimicry ring
  
  # Mimicry list
  mimicry.list <- as.character(unique(list_occ[,paste0("MR_",m)])) # 44 Mimicry rings
  
  mean_BC <- NA
  for (i in 1:length(mimicry.list)) # Per mimicry rings
  { 
    # i <-  1
    ring <- mimicry.list[i]
    
    # Get names and indices of all units/OMUs for this ring
    tags <- unique(as.character(list_occ[,tag][shuffle.list.unit$Ring == ring]))
     tags <- tags[tags %in% names(OMU_proba_stack)]
    
    index <- which(names(OMU_proba_stack) %in% tags)
    
    if (length(tags) < 2) # Case with only one OMU in the mimicry ring. Impossible to compute pairwise distances
    { 
      mat.index <- data.frame(matrix(nrow = 2, ncol = 0)) # Empty df of pairs coordinates
      save(mat.index, file = paste0("../outputs/Community_Structure/Permutations/BC_mimicry_ring_mat/simul_mat.index.",ring,"_",typename,"_",m,".RData")) # Save temp mat indices df to be used later to merge for all rings
      mean_BC[i] <- NA
    } else { # Case with at least 2 OMUs
      mat.index <- combn(x = index, m = 2, FUN = c) # Get all combinations possibles for pairs of OMUs indices
      save(mat.index, file = paste0("../outputs/Community_Structure/Permutations/BC_mimicry_ring_mat/simul_mat.index.",ring,"_",typename,"_",m,".RData")) # Save temp mat indices df to be used later to merge for all rings
      BC <- NA # Initiate the vector used to store all BC values
      for(j in 1:ncol(mat.index)) # For each pair of OMUs
      {
        BC[j] <- unit_BC_dist_mat[mat.index[1,j],mat.index[2,j]] # Extract Bray-Curtis index from the complete matrix of BC indices
      }
      mean_BC[i]  <- mean(BC) # Compute mean BC for all pairs of this mimicry ring and store it in final vector
    }
    
    # print(i)
  }
  names(mean_BC) <- mimicry.list
  mean_BC_null <- rbind(mean_BC_null,mean_BC) # Store the mean BC vector into the matrix of simulations, as a row
  
  # Retrieve all mimic coordinates
  all_mimic_mat_index <- data.frame(matrix(ncol = 0, nrow = 2)) # Generate empty df to store indices of pairs of comimics
  for (i in 1:length(mimicry.list)) { # Per mimicry rings
    ring <- mimicry.list[i]
    load(file =  paste0("../outputs/Community_Structure/Permutations/BC_mimicry_ring_mat/simul_mat.index.",ring,"_",typename,"_",m,".RData")) # Load the matrix of indices of pairs of comimics for this ring
    all_mimic_mat_index <- cbind(all_mimic_mat_index,mat.index) # Merge them all in one df
  }
  # dim(all_mimic_mat_index) # 14 659 pairs of mimic units
  
  # Retrieve all mimic values and non-co-mimic BC values at the same time
  BC_mimic <- NA # Initiate final vector to store BC values for comimics
  unit_BC_dist_mat_no_mimic <- unit_BC_dist_mat # Copy matrix of all BC indices for all pairs of OMUs
  for(j in 1:ncol(all_mimic_mat_index)) # For all pairs of comimics
  {
    BC_mimic[j] <- unlist(unit_BC_dist_mat[all_mimic_mat_index[1,j],all_mimic_mat_index[2,j]]) # Extract BC index for this pair of comimics
    unit_BC_dist_mat_no_mimic[all_mimic_mat_index[1,j],all_mimic_mat_index[2,j]] <- NA # Remove BC value of comimics from matrix of non-comimics pairs
  }
  # length(BC_mimic) # 14 659 pairs of mimic units
  
  # Retrieve all non-mimic values
  BC_no_mimic <- unit_BC_dist_mat_no_mimic[upper.tri(unit_BC_dist_mat_no_mimic)] # Extract only one side of the triangle to avoid duplicate values of pairs
  BC_no_mimic <- na.omit(BC_no_mimic) # Remove NA (the comimics pairs)
  # length(BC_no_mimic) # 291 494 pairs of non-mimic units
  
  # Save global mean computation into final vectors
  BC_mimic_null[k] <- mean(BC_mimic)
  BC_no_mimic_null[k] <- mean(BC_no_mimic)
  
  cat(paste0(Sys.time(), " - Simul n°", k," out of 1000\n"))
  save(mean_BC_null, BC_mimic_null, BC_no_mimic_null, file = paste0("../outputs/Community_Structure/Permutations/All_simul_mean_BC_",typename,"_",m,".RData"))
}

summary(mean_BC_null)     # Per mimicry ring
summary(BC_mimic_null)    # For all comimic pairs
summary(BC_no_mimic_null) # For all non-comimic pairs
print(paste0("Done for all ",typename))
}

##### 5/ Plot distri of null mean BC ####
for (k in 1:2) {
  if(k==1)
  {mod=com_unit_mat
  modname="com_unit_mat"
  typename="OMU"
  list_type=list_OMU
  list_type <- data.frame(unit = list_type, Ring = str_split_fixed(list_type, "[.]", n = 3)[,3])}
  else {mod=com_ssp_mat[, v==FALSE]
  modname="com_ssp_mat"
  typename="ssp"
  list_type=list_occ[v==FALSE,]}
### 5.1/ Plot for all comimics ####
  


load(file = paste0("../outputs/Community_Structure/All_Global_BC_",typename,"_",m,".RData")) # Load mean BC obs values 
load(file = paste0("../outputs/Community_Structure/Permutations/All_simul_mean_BC_",typename,"_",m,".RData"))
pdf(file = paste0("../outputs/Community_Structure/BC_mimic_null",typename,"_",m,".pdf"), height = 5.3, width = 6.5)

original_ext_margins <- par()$oma
original_int_margins <- par()$mar
par(oma = c(0,0,0,0), mar = c(5.1,8,4.1,4))

hist(x = c(BC_mimic_null, Global_mimic_mean_BC), breaks = 40, freq = TRUE, col = "gray",
     #xlim = c(0.65, 0.96),
     #ylim = c(0, 400),
     main = "Distribution of mean pairwise BC indices\nof co-mimetic OMUs\nunder null Hypothesis",
     xlab = "Mean Bray-Curtis Index",
     cex.axis = 1.3, cex.lab = 1.4, cex.main = 1.2, lwd = 2)

arrows(Global_mimic_mean_BC + 0.0007, 75, Global_mimic_mean_BC+ 0.0007, 10, length = 0.1, lwd = 2)  # Draw arrow above mean BC obs
abline(v = mean(c(BC_mimic_null, Global_mimic_mean_BC), na.rm=T), lwd = 2, lty = 2) # Add vertical line for mean value
abline(v = quantile(c(BC_mimic_null, Global_mimic_mean_BC), 0.05, na.rm=T), lwd = 2, lty = 2, col = "red") # Add vertical line for 95% value

legend(legend = c(paste0("Mean = ", format(round(mean(c(BC_mimic_null, Global_mimic_mean_BC), na.rm=T),3), nsmall = 3)), 
                  paste0("CI 5% = ", round(quantile(c(BC_mimic_null, Global_mimic_mean_BC), 0.05, na.rm=T),3))), 
       x = "topleft", inset = c(0, 0.17), 
       lty = 2 , lwd = 2, col = c("black", "red"), cex = 1.2, bty = "n")
legend(legend = c(paste0("Mean BC obs = ", round(Global_mimic_mean_BC, 3)),
                  paste0("p = 0.001")),
       x = "left", inset = c(0.00, -0.05),
       cex = 1.2, bty ="n", xjust = 1)

legend(legend = as.expression(bquote(bold("B"))), 
       x = "topleft", inset = c(-0.03, 0.001), xjust = 0.5,
       cex = 1.3, bty ="n")

par(oma = original_ext_margins, mar = original_int_margins)

dev.off()



### 5.2/ Plot distri of null BC per mimicry ring co-mimics ####

load(file = paste0("../outputs/Community_Structure/mean_BC_",typename,"_",m,".RData")) # Load mean BC obs value for each ring
load(file = paste0("../outputs/Community_Structure/Permutations/All_simul_mean_BC_",typename,"_",m,".RData") )# Load null mean BC values

# Build summary table for mimicry ring BC results at the same time
BC_ring_summary_table <- as.data.frame(matrix(ncol = 8, nrow = 39, data = NA))
names(BC_ring_summary_table) <- c("ring", "N_units", "N_pairs", "BC_obs", "mean_BC", "BC_2.5", "BC_97.5", "p_value")

for (i in 1:length(mimicry.list))  # Per mimicry ring
{
  # i <- 1
  
  BC_ring_summary_table$ring[i] <- ring <- mimicry.list[i] # Get ring name
  BC_ring_summary_table$N_units[i] <- N_units <- sum(list_type$Ring == ring) # Get number of OMUs
  BC_ring_summary_table$N_pairs[i] <- N_pairs <- N_units*(N_units-1)/2 # Get number of pairs
  
  if (is.na(mean_BC[i]))# Case for ring with no pair of OMUs (only one OMU/species)
  {
    # Plot BC null distri for this ring (i.e. NA message)
    pdf(file = paste0("../outputs/Community_Structure/Per_mimicry_ring/BC_mimic_null_",ring,"_",typename,"_",m,".pdf"), height = 5.3, width = 6.5)
    
    plot(1:100,1:100, type = "n", main = paste0("Distribution of mean pairwise Bray-Curtis indices\nof ", ring, " OMUs\nunder null Hypothesis"))
    text(x = 50, y = 50, labels = "Only one OMU for this mimicry ring \n No pair available for index computation")
    
    dev.off()
    
  } else { # Case for ring with pair(s) of OMUs 
    
    BC_ring_summary_table$BC_obs[i] <- round(mean_BC[i],3) # Get mean BC obs
    BC_ring_summary_table$mean_BC[i] <- round(mean(c(mean_BC_null[,i], mean_BC[i]), na.rm = T),3) # Get mean of mean BC null from simulations
    BC_ring_summary_table$BC_2.5[i] <- round(quantile(c(mean_BC_null[,i], mean_BC[i]), 0.025, na.rm=T),3) # Get 2.5% quantile of mean BC null from simulations
    BC_ring_summary_table$BC_97.5[i] <- round(quantile(c(mean_BC_null[,i], mean_BC[i]), 0.975, na.rm=T),3) # Get 97.5% quantile of mean BC null from simulations
    BC_ring_summary_table$p_value[i] <- round(ecdf(x = c(mean_BC_null[,i], mean_BC[i]))(mean_BC[i]),3) # Get p-value from simulations
    
    save(BC_ring_summary_table, file = paste0( "../outputs/Community_Structure/BC_ring_summary_table_",typename,"_",m,".Rdata"))
    
    # Plot BC null distri for this ring
    pdf(file = paste0("../outputs/Community_Structure/Per_mimicry_ring/BC_mimic_null_",ring,"_",typename,"_",m,".pdf"), height = 5.3, width = 6.5)
    
    hist(c(mean_BC_null[,i], mean_BC[i]), 
         breaks = seq(from = floor(floor(min(min(mean_BC_null[,i], na.rm=T), mean_BC[i])*1000)/2)/500, to = ceiling(ceiling(max(max(mean_BC_null[,i], na.rm=T), mean_BC[i])*1000)/2)/500, by = 0.002), 
         xlab = "Mean pairwise Bray-Curtis index", 
         main = paste0("Distribution of mean pairwise Bray-Curtis indices\nof ", ring," ", typename,"\nunder null Hypothesis"))
    
    # arrows(mean_BC[i] + 0.0001, 60, mean_BC[i] + 0.0001, 10, length = 0.1, lwd = 2)  # Draw arrow above mean BC obs
    abline(v = mean_BC[i], lwd = 2, lty = 2, col = "red") # Add vertical line for mean BC obs value
    
    abline(v = mean(c(mean_BC_null[,i], mean_BC[i]), na.rm = T), lwd = 2, lty = 2) # Add vertical line for mean value
    abline(v = quantile(c(mean_BC_null[,i], mean_BC[i]), 0.025, na.rm = T), lwd = 2, lty = 2, col = "grey30") # Add vertical line for 2.5% value
    abline(v = quantile(c(mean_BC_null[,i], mean_BC[i]), 0.975, na.rm = T), lwd = 2, lty = 2, col = "grey30") # Add vertical line for 97.5% value
    
    legend(legend = c(paste0("N units = ", N_units), 
                      paste0("N pairs = ", N_pairs)),
           x = "topright", xjust = 1, cex = 1, bty ="n")
    
    legend(legend = c(paste0("Mean = ", round(mean(c(mean_BC_null[,i], mean_BC[i]), na.rm = T),3)), 
                      paste0("CI 2.5% = ", round(quantile(c(mean_BC_null[,i], mean_BC[i]), 0.025, na.rm=T),3)),
                      paste0("CI 97.5% = ", round(quantile(c(mean_BC_null[,i], mean_BC[i]), 0.975, na.rm=T),3))),
           x = "topleft", cex = 1, bty ="n") 
    
    legend(legend = paste0("Mean BC obs = ", round(mean_BC[i], 3), "\n p = ", round(ecdf(x = mean_BC_null[,i])(mean_BC[i]),3)), 
           inset = c(0, 0.2), text.col = "red", x = "bottomleft", cex = 1, bty ="n")
    
    dev.off()
    
    
  }
  
  cat(paste0(i, " out of 39 - ",ring, " - Done \n"))
}

View(BC_ring_summary_table)
write.csv2(BC_ring_summary_table, file = paste0("../tables/BC_ring_summary_table_",typename,"_",m,".csv"))

##### 5/ Plot distri of null mean BC ####

### 5.1/ Plot for all comimics ####

load(file = paste0("../outputs/Community_Structure/All_Global_BC_",typename,"_",m,".RData")) # Load mean BC obs values 
load(file = paste0("../outputs/Community_Structure/Permutations/All_simul_mean_BC_",typename,"_",m,".RData")) # Load null mean BC values

pdf(file = paste0("../outputs/Community_Structure/BC_mimic_null_",typename,"_",m,".pdf", height = 5.3, width = 6.5))

original_ext_margins <- par()$oma
original_int_margins <- par()$mar
par(oma = c(0,0,0,0), mar = c(5.1,8,4.1,4))

hist(x = c(BC_mimic_null, Global_mimic_mean_BC), breaks = 40, freq = TRUE, col = "gray",
     #xlim = c(0.70, 0.96),
     #ylim = c(0, 400),
     main = "Distribution of mean pairwise BC indices\nof co-mimetic OMUs\nunder null Hypothesis",
     xlab = "Mean Bray-Curtis Index",
     cex.axis = 1.3, cex.lab = 1.4, cex.main = 1.2, lwd = 2)

arrows(Global_mimic_mean_BC + 0.0007, 75, Global_mimic_mean_BC+ 0.0007, 10, length = 0.1, lwd = 2)  # Draw arrow above mean BC obs
abline(v = mean(c(BC_mimic_null, Global_mimic_mean_BC), na.rm=T), lwd = 2, lty = 2) # Add vertical line for mean value
abline(v = quantile(c(BC_mimic_null, Global_mimic_mean_BC), 0.05, na.rm=T), lwd = 2, lty = 2, col = "red") # Add vertical line for 95% value

legend(legend = c(paste0("Mean = ", format(round(mean(c(BC_mimic_null, Global_mimic_mean_BC), na.rm=T),3), nsmall = 3)), 
                  paste0("CI 5% = ", round(quantile(c(BC_mimic_null, Global_mimic_mean_BC), 0.05, na.rm=T),3))), 
       x = "topleft", inset = c(0, 0.17), 
       lty = 2 , lwd = 2, col = c("black", "red"), cex = 1.2, bty = "n")
legend(legend = c(paste0("Mean BC obs = ", round(Global_mimic_mean_BC, 3)),
                  paste0("p = 0.001")),
       x = "left", inset = c(0.00, -0.05),
       cex = 1.2, bty ="n", xjust = 1)

legend(legend = as.expression(bquote(bold("B"))), 
       x = "topleft", inset = c(-0.03, 0.001), xjust = 0.5,
       cex = 1.3, bty ="n")

par(oma = original_ext_margins, mar = original_int_margins)

dev.off()



### 5.2/ Plot distri of null BC per mimicry ring co-mimics ####

load(file = paste0("../outputs/Community_Structure/mean_BC_",typename,"_",m,".RData")) # Load mean BC obs value for each ring
load(file = paste0("../outputs/Community_Structure/Permutations/All_simul_mean_BC_",typename,"_",m,".RData")) # Load null mean BC values

# Build summary table for mimicry ring BC results at the same time
BC_ring_summary_table <- as.data.frame(matrix(ncol = 8, nrow = 39, data = NA))
names(BC_ring_summary_table) <- c("ring", "N_units", "N_pairs", "BC_obs", "mean_BC", "BC_2.5", "BC_97.5", "p_value")

for (i in 1:length(mimicry.list))  # Per mimicry ring
{
  # i <- 1
  
  BC_ring_summary_table$ring[i] <- ring <- mimicry.list[i] # Get ring name
  BC_ring_summary_table$N_units[i] <- N_units <- sum(list_type$Ring == ring) # Get number of OMUs
  BC_ring_summary_table$N_pairs[i] <- N_pairs <- N_units*(N_units-1)/2 # Get number of pairs
  
  if (is.na(mean_BC[i]))# Case for ring with no pair of OMUs (only one OMU/species)
  {
    # Plot BC null distri for this ring (i.e. NA message)
    pdf(file = paste0("../outputs/Community_Structure/Per_mimicry_ring/BC_mimic_null_",ring,"_",typename,"_",m,".pdf"), height = 5.3, width = 6.5)
    
    plot(1:100,1:100, type = "n", main = paste0("Distribution of mean pairwise Bray-Curtis indices\nof ", ring, " ", typename, "\nunder null Hypothesis"))
    text(x = 50, y = 50, labels = "Only one OMU for this mimicry ring \n No pair available for index computation")
    
    dev.off()
    
  } else { # Case for ring with pair(s) of OMUs 
    
    BC_ring_summary_table$BC_obs[i] <- round(mean_BC[i],3) # Get mean BC obs
    BC_ring_summary_table$mean_BC[i] <- round(mean(c(mean_BC_null[,i], mean_BC[i]), na.rm = T),3) # Get mean of mean BC null from simulations
    BC_ring_summary_table$BC_2.5[i] <- round(quantile(c(mean_BC_null[,i], mean_BC[i]), 0.025, na.rm=T),3) # Get 2.5% quantile of mean BC null from simulations
    BC_ring_summary_table$BC_97.5[i] <- round(quantile(c(mean_BC_null[,i], mean_BC[i]), 0.975, na.rm=T),3) # Get 97.5% quantile of mean BC null from simulations
    BC_ring_summary_table$p_value[i] <- round(ecdf(x = c(mean_BC_null[,i], mean_BC[i]))(mean_BC[i]),3) # Get p-value from simulations
    
    save(BC_ring_summary_table, file =paste0( "../outputs/Community_Structure/BC_ring_summary_table_",typename,"_",m,".Rdata"))
    
    # Plot BC null distri for this ring
    pdf(file = paste0("../outputs/Community_Structure/Per_mimicry_ring/BC_mimic_null_",ring,"_",typename,"_",m,".pdf"), height = 5.3, width = 6.5)
    
    hist(c(mean_BC_null[,i], mean_BC[i]), 
         breaks = seq(from = floor(floor(min(min(mean_BC_null[,i], na.rm=T), mean_BC[i])*1000)/2)/500, to = ceiling(ceiling(max(max(mean_BC_null[,i], na.rm=T), mean_BC[i])*1000)/2)/500, by = 0.002), 
         xlab = "Mean pairwise Bray-Curtis index", 
         main = paste0("Distribution of mean pairwise Bray-Curtis indices\nof ", ring, " ", typename, "s\nunder null Hypothesis"))
    
    # arrows(mean_BC[i] + 0.0001, 60, mean_BC[i] + 0.0001, 10, length = 0.1, lwd = 2)  # Draw arrow above mean BC obs
    abline(v = mean_BC[i], lwd = 2, lty = 2, col = "red") # Add vertical line for mean BC obs value
    
    abline(v = mean(c(mean_BC_null[,i], mean_BC[i]), na.rm = T), lwd = 2, lty = 2) # Add vertical line for mean value
    abline(v = quantile(c(mean_BC_null[,i], mean_BC[i]), 0.025, na.rm = T), lwd = 2, lty = 2, col = "grey30") # Add vertical line for 2.5% value
    abline(v = quantile(c(mean_BC_null[,i], mean_BC[i]), 0.975, na.rm = T), lwd = 2, lty = 2, col = "grey30") # Add vertical line for 97.5% value
    
    legend(legend = c(paste0("N units = ", N_units), 
                      paste0("N pairs = ", N_pairs)),
           x = "topright", xjust = 1, cex = 1, bty ="n")
    
    legend(legend = c(paste0("Mean = ", round(mean(c(mean_BC_null[,i], mean_BC[i]), na.rm = T),3)), 
                      paste0("CI 2.5% = ", round(quantile(c(mean_BC_null[,i], mean_BC[i]), 0.025, na.rm=T),3)),
                      paste0("CI 97.5% = ", round(quantile(c(mean_BC_null[,i], mean_BC[i]), 0.975, na.rm=T),3))),
           x = "topleft", cex = 1, bty ="n") 
    
    legend(legend = paste0("Mean BC obs = ", round(mean_BC[i], 3), "\n p = ", round(ecdf(x = mean_BC_null[,i])(mean_BC[i]),3)), 
           inset = c(0, 0.2), text.col = "red", x = "bottomleft", cex = 1, bty ="n")
    
    dev.off()
    
    
  }
  
  cat(paste0(i, " out of 39 - ",ring, " - Done \n"))
}

View(BC_ring_summary_table)
write.csv2(BC_ring_summary_table, file =paste0( "../tables/BC_ring_summary_table_",typename,"_",m,".csv"))

print(paste0("Done for all ",typename))
}


# #Plot Bray curtis valors with distributions
# library(raster)
# library(rangeBuilder)
# main_title_cex = 1                # Main title size
# 
# xlim = c(-5457, 4953)   # Limit of plot on x-axis (Longitude)
# ylim = c(-4495, 5705)    # Limit of plot on y-axis (Latitude)
# axis_cex = 1.4             # Axes size
# 
# xlab = ""                # X-axis label
# ylab = ""                # Y-axis label
# x_axis_breaks = c(-3930, -2170, -420, 1500, 3050)          # X-axis tick breaks
# y_axis_breaks = c(-3650, -2450, -1220, 0, 1230, 2445, 3660, 4890)       # Y-axis tick breaks
# x_axis_labels = c("120°E", "100°E", "80°E", "60°E", "40°E")    # X-axis tick labels
# y_axis_labels = c("30°S", "20°S", "10°S", "0°", "10°N", "20°N", "30°N", "40°N")    # Y-axis tick labels
# 
#           # Legend title
# legend_title_cex = 1.3   # Legend title size
# legend_title_x = -3550   # Legend title x position
# legend_title_y = 430     # Legend title y position
# legend_cex = 1.4         # Legend size         # Legend tick positions
# legend_location = c(-4100, -3800, -3950, 0)  # Legend position
# 
# scale_bar_position = c(-2600, -4000) # Scale bar position
# 
# arrow_scale = 0.55        # North arrow size
# arrow_padin = c(0.15, 0.15) # North arrow position adjustement
# 
# facet_letter = ""               # Small case letter for facet
# facet_letter_col = "black"         # Color of case letter for facet
# facet_letter_cex = 2.2             # Size of small case letter for facet
# facet_letter_inset = c(0, -0.008)
# 
# 
# Hmm<-readRDS("../outputs/By_unit/Heliconius.melpomene.malleti/all_EM_Jaccard_buffer_80.rds")[[1]]
# Hab<-readRDS("../outputs/By_unit/Heliconius.aoede.bartletti/all_EM_Jaccard_buffer_80.rds")[[1]]
# Hee<-readRDS("../outputs/By_unit/Heliconius.erato.emma/all_EM_Jaccard_buffer_80.rds")[[1]]
# Hsm<-readRDS("../outputs/By_unit/Heliconius.sara.magdalena/all_EM_Jaccard_buffer_80.rds")[[1]]
# 
# load("../input_data/envData/continent_mask.RData")
# load("../input_data/envData/crop_shape.RData")
# pal_bl_red_Mannion<-readRDS("../Maps/pal_bl_red_Mannion.rds")
# sea_shp<-readRDS(file="../input_data/Map_stuff/sea_shp.RDS")
# # Load mask for continent borders, plot border, and grid
# grid_Mollweide_out <- readRDS(file = "../input_data/Map_stuff/grid_Mollweide_out.rds")
# large_bg_mask_Mollweide <- readRDS(file = "../input_data/envData/crop_shape.RDS")
# bbox_sp_Mollweide <- readRDS(file = "../input_data/Map_stuff/bbox_sp_Mollweide.rds")


# pdf(file = paste0("../Maps/Bray_Curtis_maps.pdf"), height = 12, width = 12)
# 
# 
# internal_margins <- par()$mar
# # par(mar = c(3.1, 3.5, 3.5, 2.1))
# par(mar = c(3.1, 3.1, 2.7, 1.6))
# par(mfrow = c(2, 2))
# 
# 
# ##Hmm
#      image(Hmm, col= rev(terrain.colors(10)) , legend=FALSE, main = 
#         expression(paste("Predictions for ", italic("Heliconius melpomene maletti "))), cex.axis = 1.4, cex.main = 1.2, axes=FALSE,
#       ylab = "", xlab = "")
#      
#      plot(crop_shape, lwd = 1.2, border = "grey20", add = TRUE, legend=F)
#      plot(sea_shp, legend=F, col="#E1f1f1", add=T )
# plot(large_bg_mask_Mollweide, lwd = 1, col = "grey20", add = T)
# plot(grid_Mollweide_out, lty = 92, col = "grey80",legend=F,  add = T)
# plot(bbox_sp_Mollweide, lwd = 2, border = "black", col = NA, legend=F, add = T)
# 
# axis(side = 1, at = x_axis_breaks, labels = x_axis_labels, cex.axis = axis_cex, lwd = 0.2, lwd.ticks = 1, gap.axis = 0, padj = 0.5)
# axis(side = 2, at = y_axis_breaks, labels = y_axis_labels, cex.axis = axis_cex, lwd = 0.2, lwd.ticks = 1, gap.axis = 0)
# addRasterLegend(Hmm, locs = seq(0, 0.85, 0.1), cex.axis = 1.2, ramp = rev(terrain.colors(10)), ncolors = 50, border = T, location = c(-4000, -3000, -3000, 0))
#      graphics::text(x = -3500, y = 500, font = 2, cex = 1.2, label = "Habitat suitability")
# 
#      ##Hdd
#      image(Hab, col= rev(terrain.colors(10)) , legend=FALSE, main = 
#         expression(paste("Predictions for ", italic("Heliconius aoede bartletti "), "BC=0.16")), cex.axis = 1.4, cex.main = 1.2, axes=FALSE,
#       ylab = "", xlab = "")
#      
#      plot(crop_shape, lwd = 1.2, border = "grey20", add = TRUE, legend=F)
#      plot(sea_shp, legend=F, col="#E1f1f1", add=T )
# plot(large_bg_mask_Mollweide, lwd = 1, col = "grey20", add = T)
# plot(grid_Mollweide_out, lty = 92, col = "grey80",legend=F,  add = T)
# plot(bbox_sp_Mollweide, lwd = 2, border = "black", col = NA, legend=F, add = T)
# 
# axis(side = 1, at = x_axis_breaks, labels = x_axis_labels, cex.axis = axis_cex, lwd = 0.2, lwd.ticks = 1, gap.axis = 0, padj = 0.5)
# axis(side = 2, at = y_axis_breaks, labels = y_axis_labels, cex.axis = axis_cex, lwd = 0.2, lwd.ticks = 1, gap.axis = 0)
# addRasterLegend(Hab, locs = seq(0, 0.85, 0.1), cex.axis = 1.2, ramp = rev(terrain.colors(10)), ncolors = 50, border = T, location = c(-4000, -3000, -3000, 0))
#      graphics::text(x = -3500, y = 500, font = 2, cex = 1.2, label = "Habitat suitability")
#      
# ##Hap
#      image(Hee, col= rev(terrain.colors(10)) , legend=FALSE, main = 
#         expression(paste("Predictions for ", italic("Heliconius erato emma "), "BC=0.73")), cex.axis = 1.4, cex.main = 1.2, axes=FALSE,
#       ylab = "", xlab = "")
#      
#      plot(crop_shape, lwd = 1.2, border = "grey20", add = TRUE, legend=F)
#      plot(sea_shp, legend=F, col="#E1f1f1", add=T )
# plot(large_bg_mask_Mollweide, lwd = 1, col = "grey20", add = T)
# plot(grid_Mollweide_out, lty = 92, col = "grey80",legend=F,  add = T)
# plot(bbox_sp_Mollweide, lwd = 2, border = "black", col = NA, legend=F, add = T)
# 
# axis(side = 1, at = x_axis_breaks, labels = x_axis_labels, cex.axis = axis_cex, lwd = 0.2, lwd.ticks = 1, gap.axis = 0, padj = 0.5)
# axis(side = 2, at = y_axis_breaks, labels = y_axis_labels, cex.axis = axis_cex, lwd = 0.2, lwd.ticks = 1, gap.axis = 0)
# addRasterLegend(Hee, locs = seq(0, 0.85, 0.1), cex.axis = 1.2, ramp = rev(terrain.colors(10)), ncolors = 50, border = T, location = c(-4000, -3000, -3000, 0))
#      graphics::text(x = -3500, y = 500, font = 2, cex = 1.2, label = "Habitat suitability")
#      
# ##Hab
#      image(Hsm, col= rev(terrain.colors(10)) , legend=FALSE, main = 
#         expression(paste("Predictions for ", italic("Heliconius sara magdalena "), "BC=0.94")), cex.axis = 1.4, cex.main = 1.2, axes=FALSE,
#       ylab = "", xlab = "")
#      
#      plot(crop_shape, lwd = 1.2, border = "grey20", add = TRUE, legend=F)
#      plot(sea_shp, legend=F, col="#E1f1f1", add=T )
# plot(large_bg_mask_Mollweide, lwd = 1, col = "grey20", add = T)
# plot(grid_Mollweide_out, lty = 92, col = "grey80",legend=F,  add = T)
# plot(bbox_sp_Mollweide, lwd = 2, border = "black", col = NA, legend=F, add = T)
# 
# axis(side = 1, at = x_axis_breaks, labels = x_axis_labels, cex.axis = axis_cex, lwd = 0.2, lwd.ticks = 1, gap.axis = 0, padj = 0.5)
# axis(side = 2, at = y_axis_breaks, labels = y_axis_labels, cex.axis = axis_cex, lwd = 0.2, lwd.ticks = 1, gap.axis = 0)
# addRasterLegend(Hsm, locs = seq(0, 0.85, 0.1), cex.axis = 1.2, ramp = rev(terrain.colors(10)), ncolors = 50, border = T, location = c(-4000, -3000, -3000, 0))
#      graphics::text(x = -3500, y = 500, font = 2, cex = 1.2, label = "Habitat suitability")
#  
# dev.off()     
}
```


