---
title: "27_Mimicry_rings_tables_generation"
author: "Eddie Pérochon"
date: "2022-07-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


##### Script 27: Pages with picures of each mimicry rings#####

/!\ Pictures not accessible in the supplementaries  /!\

###################################################
#      Authors: Eddie Pérochon & Maël Doré        #
#      Contact: eddie.perochon@hotmail.com        #
###################################################


### Goals = 
# Create pages to illustrate Heliconiini mimicry rings
 
### Inputs
# Pictures of each taxa, from Chris Jiggin, Blanca Huertas, butterfliesofamerica.com

###

### Outputs
#Pages with pictures of each mimicry rings

###


```{r}
rm(list=ls())
##Charge useful objects
#Ssp table with OMUs
picture_correspondance<-readxl::read_excel("Excels d'info/Mimicry-rings.xlsx", 
    sheet = "Mimicry_ring_pictures")
picture_correspondance$Colonne5[picture_correspondance$Colonne5=="Red band"]<-"Redband"

#List Mimicry rings
mimicry_rings_list<-unique(picture_correspondance$Colonne5)

```

```{r}
#plot jpg function
plot_jpeg = function(path, add=FALSE)
{
  require('jpeg')
  jpg = readJPEG(path, native=T) # read the file
  res = dim(jpg)[2:1] # get the resolution, [x, y]
  if (!add) # initialize an empty plot area if add==FALSE
    plot(1,1,xlim=c(1,res[1]),ylim=c(1,res[2]),asp=1,type='n',xaxs='i',yaxs='i',xaxt='n',yaxt='n',xlab='',ylab='',bty='n')
  rasterImage(jpg,1,1,res[1],res[2])
}
```

```{r}
#Creating each table of pictures

for(i in 1:length(mimicry_rings_list))
{
  ring<-mimicry_rings_list[i]
  list_ssp_ring<-picture_correspondance$Pic[picture_correspondance$Colonne5==ring]
  list_names_ring<-picture_correspondance$fullname[picture_correspondance$Colonne5==ring]

pdf(paste0("../Photo Heliconiini/Example for each mimicry ring/Planches/",ring,".pdf"), height = 20, width = 8)

internal_margins <- par()$mar
par(mar = c(1.5, 1.5, 1.5, 1.5))
par(mfrow= c(10, 4))


if(is.na(match(ring, c("Chestertonii", "Heurippa", "Cretacea")))==FALSE) #cases with 1 ssp in the ring, not in the same folder
{
  main<-list_names_ring
  ssp<-list_ssp_ring
    plot_jpeg(paste0("../Photo Heliconiini/Mimicry_ring_mur/",ssp))
    title(main, line = -11, cex.main=0.8)
    dev.off() 
    print(paste0("Done for ",ring," ",i,"/",length(mimicry_rings_list)))
    next
}

  for (j in 1:length(list_ssp_ring))
  {
    ssp <- list_ssp_ring[j]
    main <- list_names_ring[j]
    plot_jpeg(paste0("../Photo Heliconiini/Mimicry_ring_mur/", ring, "/", ssp))
    title(main, line = -11, cex.main = 0.8)
  }

par(mar = internal_margins)
par(mfrow = c(1, 1))

dev.off()
print(paste0("Done for ",ring," ",i,"/",length(mimicry_rings_list)))
  
}
```

