---
title: "28_IthovsHelico_rings_maps"
author: "Eddie Pérochon"
date: "2023-04-07"
output: html_document
---

##### Script 28: Bivariate maps of habitat suitability for intertribes comimics#####

###################################################
#      Authors: Eddie Pérochon & Maël Doré        #
#      Contact: eddie.perochon@hotmail.com        #
###################################################


### Goals = 
# Plot habitat suitability for 3 comimetic groups of OMUs between Ithomiini & Heliconiini

### Inputs

# Heliconiini Mimicry ring maps from script 18
# Ithomiini Mimicry ring maps from Doré et al. 2020 (Diversity & Distributions)

###

### Outputs

#Maps of habitat suitability for intertribes comimics

###

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
rm(list = ls())
gc()

library(raster)
library(stringr)
library(dplyr)
# library(rgeos)
library(biscale)
library(cowplot)
library(sf)
library(ggplot2)
library(bivariatemaps)
library(png)
library(ape)
# library(ggtree)
library(phytools)
library(TreeTools)


```

```{r}

# New rings to plot: EXCELSA, PAVONII, MAELUS

# names_v <- c( "MOTHONE", "MANTINEUS", "MAMERCUS")
# names_clean <- c("MOTHONE habitat suitability", "MANTINEUS  habitat suitability", "MAMERCUS habitat suitability")
# names_clean_lg <- c("MOTHONE\n habitat suitability", "MANTINEUS\n  habitat suitability", "MAMERCUS\n habitat suitability")

names_v <- c( "EXCELSA", "PAVONII", "MAELUS")
names_clean <- c("EXCELSA habitat suitability", "PAVONII  habitat suitability", "MAELUS habitat suitability")
names_clean_lg <- c("EXCELSA\n habitat suitability", "PAVONII\n  habitat suitability", "MAELUS\n habitat suitability")

HeIT_proba_ring <- readRDS("../input_data/Species_data/HeIt_ring_proba_stack_ss.RDS")

shared_rings <- c("EURIMEDIA", "EXCELSA", "HERMIAS", "HUMBOLDT", "LYSIMNIA", "MAELUS", "MAMERCUS", "MOTHONE", "ORESTES", "PAVONII")

ITHO_rings_all <- HeIT_proba_ring[[paste0(shared_rings, ".ITHO")]]
pdf(file = "../maps/Shared_rings_Itho.pdf", height = 8, width = 12)
plot(ITHO_rings_all)
dev.off()

HELICO_rings_all <- HeIT_proba_ring[[paste0(shared_rings, ".HELICO")]]
pdf(file = "../maps/Shared_rings_Helico.pdf", height = 8, width = 12)
plot(HELICO_rings_all)
dev.off()

ITHO_rings <- HeIT_proba_ring[[c("EXCELSA.ITHO", "PAVONII.ITHO", "MAELUS.ITHO")]]

HEL_rings <- HeIT_proba_ring[[c("EXCELSA.HELICO", "PAVONII.HELICO", "MAELUS.HELICO")]]

# Load mask for continent borders, plot border, and grid
grid_Mollweide_out <- readRDS(file = "../input_data/Biogeographic_data/grid_Mollweide_out.rds")
large_bg_mask_Mollweide <- readRDS(file = "../input_data/envData/crop_shape.RDS")
bbox_sp_Mollweide <- readRDS(file = "../input_data/Biogeographic_data/bbox_sp_Mollweide.rds")
sea_shp <- readRDS(file = "../input_data/Biogeographic_data/sea_shp.RDS")


```


```{r}

### Generate bivariate legends

# Load custom functions

source("../functions/colmat_modified.R")
source("../functions/biv_map_modified.R")
source("../functions/custom_Bivariates_maps_mollweide.R")
source("../functions/add_bivar_legend.R")

for(i in 1:length(names_v))
{
names <- names_v[i]
  
  col.matrix <- colmat_modif(nquantiles=4, upperleft="#f3b300", upperright="#000000", bottomleft="#f3f3f3", bottomright="#509dc2", xlab=paste0(names, " Heliconiini habitat suitability"), ylab= paste0(names, "Ithomiini habitat suitability "), valuesx = HEL_rings[[i]], valuesy =  ITHO_rings[[i]])
  
   
  bivmap <- biv_map_modified(HEL_rings[[i]], ITHO_rings[[i]], col.matrix, nquantiles = 4)
  #   
  assign(paste0(names_v[i], "_bivmap"), bivmap)
  
  #Add grey for 0x0 as last color
  col.matrix_v <- as.vector(col.matrix)
  col.matrix_v[ length(col.matrix) + 1] <-  "lightgrey" #"#DEE1EB"
  
  assign(paste0(names_v[i], "_colmat"), col.matrix)
  assign(paste0(names_v[i], "_colv"), col.matrix_v)
} 


for(l in 1:3)
{
name_code <- names_v[l]
col.matrix =   get(paste0(name_code, "_colmat"))

scale_decimals <- 1 # General case, not possible to have more numbers so for big number, no decimals


add_bivar_legend(rasterx = HEL_rings[[l]],
                 rastery = ITHO_rings[[l]],
                 color.matrix = col.matrix,
                 nquantiles = 4,
                 xlab = substitute(paste(bold("Heliconiini"))),
                 ylab = substitute(paste(bold("Ithomiini"))),
                 pngname = paste0("../maps/Map_legends/",name_code,"_Bivmap_legend.png"),
                 scaledeci = scale_decimals)
}                 




```

```{r}

# Mollweide map, final plot


pdf("../maps/BivarMap_rings.pdf", height = 4, width = 12)
par(mar = c(3.1, 3.1, 2.7, 1.6))
par(mfrow = c(1, 3))


for (l in 1:3)
{
name_code <- names_v[l]
main <- names_clean[l]
name_clean_l <- names_clean_lg[l]

map <- get(paste0(name_code, "_bivmap"))
palette_bv <- unique(get(paste0(name_code, "_colv")))
  
 image(sea_shp,  col="#E1f1f1", #background
         xlim = c(-5457, 4953), ylim = c(-4495, 5705), axes = F,
         xlab = "", ylab = "")
# Add background, borders and graticules
  plot(bbox_sp_Mollweide, lwd = 2, border = "black", col = NA, legend=F, add = T)
  plot(grid_Mollweide_out, lty = 92, col = "grey80",legend=F,  add = T)
  par(new=TRUE)

Bivar_map_Mollweide(x = map, color_palette = palette_bv, main_title = paste0(main), legend_title = name_clean_l, facet_letter = paste0("(",letters[l],")")) 
plot(large_bg_mask_Mollweide, lwd = 1, col = "grey20", add = T)
par(new=TRUE)

legend_biv <- readPNG(source = paste0("../maps/Map_legends/",name_code,"_Bivmap_legend.png"))

par(new = TRUE)
rasterImage(legend_biv, xleft = -5500, ybottom = -4400, xright = -1000, ytop = 100)


}
dev.off()


```